### 2016-11-22 practical_2/report/report_lastname.tex
update

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2016
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2016}

\usepackage[final]{nips_2016}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2016}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{fancyvrb,xcolor}
\usepackage{graphicx}

\title{Report for the Deep Learning Course Assignment 2 }

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  Georgios Methenitis \\
  \texttt{georgios.methenitis@cwi.nl}
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\begin{abstract}
In this assignment I got familiar with TensorFlow. I created a single hidden layer network with ReLU activation function to learn features for the CIFAR10 dataset.
\end{abstract}

\section{Task 1}
\begin{enumerate}
\item 
\item There are two ways to declare variable in TensorFlow:
\begin{itemize}
\item \begin{small}
\begin{verbatim}
var = tf.get_variable("var_name", shape=[..., ...])
\end{verbatim}
\end{small}
\item \begin{small}
\begin{verbatim}
var = tf.Variable(tf.zeros([..., ...]), name="var_name")
\end{verbatim}
\end{small}
\end{itemize}

\item The command \texttt{tf.shape(x)} returns the shape of the input of tensor \texttt{x} in an 1-D vector, while \texttt{x.get\_shape()} return the size of the tensor.
\item
\item
\item
\item
\item
\item
\item
\end{enumerate}

\section{Task 2}
In this task I implemented the following functions in \texttt{mlp.py}, more specifically the \texttt{inference}, \texttt{loss}, and \texttt{accuracy}.

\begin{small}
\begin{verbatim}
  def inference(self, x):
    with tf.variable_scope('hidden', reuse=None):
      W = tf.get_variable("weights", shape=[x.get_shape()[1], self.n_hidden[0]],
       initializer=self.weight_initializer, regularizer=self.weight_regularizer)
      tf.histogram_summary("hidden_weights", W)
      b = tf.Variable(tf.zeros([self.n_hidden[0]]), name="bias")
      tf.histogram_summary("hidden_bias", b)

    with tf.variable_scope('output', reuse=None):
      w_out = tf.get_variable("weights", shape=[self.n_hidden[0], self.n_classes],
       initializer=self.weight_initializer, regularizer=self.weight_regularizer)
      tf.histogram_summary("output_weights", w_out)
      b_out = tf.Variable(tf.zeros([self.n_classes]), name="bias")
      tf.histogram_summary("output_bias", b_out)

    with tf.name_scope('relu_layer'):
      input = self.activation_fn(tf.matmul(x, W) + b)
    with tf.name_scope('linear_layer'):
      output = tf.matmul(input, w_out) + b_out

    return output

  def loss(self, logits, labels):

    loss = tf.reduce_mean(tf.nn.softmax_cross_entropy_with_logits(logits, labels, name=None))
    with tf.variable_scope("hidden", reuse=True):
      loss += 0.5 * tf.reduce_sum(tf.get_variable("weights")**2)
    with tf.variable_scope("output", reuse=True):
      loss += 0.5 * tf.reduce_sum(tf.get_variable("weights")**2)

    return loss

  def accuracy(self, logits, labels):
    correct_prediction = tf.equal(tf.argmax(labels, 1), tf.argmax(logits, 1))
    accuracy = tf.reduce_mean(tf.cast(correct_prediction, tf.float32))
    return accuracy
\end{verbatim}
\end{small}
I also implemented the function \texttt{train} in the file \texttt{train\_mlp.py}:
\begin{small}
\begin{verbatim}
def train():
  # placeholder for input and output tensors allowing to create operations and the computation graph
  x = tf.placeholder(tf.float32, shape=[None, 3072])
  y_ = tf.placeholder(tf.float32, shape=[None, 10])

  # model, namescopes for summary
  model = MLP()
  x_ = model.inference(x)
  with tf.name_scope('loss'):
    loss = model.loss(x_, y_)
  with tf.name_scope('accuracy'):
    accuracy = model.accuracy(x_, y_)
  with tf.name_scope('train_step'):
    train_step = tf.train.GradientDescentOptimizer(LEARNING_RATE_DEFAULT).minimize(loss)

  # session
  init = tf.initialize_all_variables()
  sess = tf.Session()
  sess.run(init)

  # merged summary for the graph, the loss and accuracy
  tf.scalar_summary('accuracy', accuracy)
  tf.scalar_summary('loss', loss)
  tf.histogram_summary("logits", x_) # logits histogram
  merged = tf.merge_all_summaries()

  train_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/train', sess.graph)
  test_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/test', sess.graph)

  for i in range(1, MAX_STEPS_DEFAULT+1):
      batch_xs, batch_ys = cifar10.train.next_batch(BATCH_SIZE_DEFAULT)
      __, Summary, l, acc = sess.run([train_step, merged, loss, accuracy],
      feed_dict={x: batch_xs, y_: batch_ys})
      train_writer.add_summary(Summary, i)

      if i % 100 == 0.0:
          batch_xs, batch_ys = cifar10.test.images, cifar10.test.labels
          __, Summary, l, acc = sess.run([train_step, merged, loss, accuracy],
           feed_dict={x: batch_xs, y_: batch_ys})
          test_writer.add_summary(Summary, i)

  train_writer.close()
\end{verbatim}
\end{small}

Figure~\ref{fig:acclosstrain} presents the accuracy and the loss in the training set recorded for every epoch.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{loss.png}\	
\includegraphics[width=0.45\textwidth]{accuracy.png}
\caption{Recorded accuracy and loss for the training set.}
\label{fig:acclosstrain}
\end{figure}

Figure~\ref{fig:acclosstest} presents the accuracy and the loss in the test set recorded for every 100-epochs.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{accuracy_t.png}\	
\includegraphics[width=0.45\textwidth]{loss_t.png}
\caption{Recorded accuracy and loss for the test set.}
\label{fig:acclosstest}
\end{figure}

Figure~\ref{fig:graph} presents the graph of the created model as this is illustrated by TensorBoard.

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{graph.png}
\caption{Graph of the model.}
\label{fig:graph}
\end{figure}

Figure~\ref{fig:histogramsunits} presents the histograms of the weights and the biases in every unit of the model, in the hidden and the output units respectively.

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{hidden_weights.png}
\includegraphics[width=0.3\textwidth]{hidden_bias.png}
\includegraphics[width=0.3\textwidth]{output_weights.png}
\includegraphics[width=0.3\textwidth]{output_bias.png}
\caption{Histograms of weights and bias in the hidden layer, and weights and bias in the output linear layer.}
\label{fig:histogramsunits}
\end{figure}

Figure~\ref{fig:histogramlogits} presents the histogram of the logits.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{logits.png}
\caption{Histograms of logits.}
\label{fig:histogramlogits}
\end{figure}

\section{Conclusion}
Should contain conclusion of this study.
For example, you can try to answer the following questions.
What was done during this assignment? What features of TensorBoard were positive and what were negative for implementing MLP model and performing the experiments?
What are the main insights you got from the study of the MLP model on CIFAR10 dataset?

\end{document}

### 2016-11-22 practical_2/mlp.py

@@ -91,16 +91,46 @@ class MLP(object):
     ########################
     # PUT YOUR CODE HERE  #
     #######################
+    # with tf.variable_scope('hidden', reuse=None):
+    #   W = tf.get_variable("weights", shape=[x.get_shape()[1], self.n_hidden[0]], initializer=self.weight_initializer, regularizer=self.weight_regularizer)
+    #   tf.histogram_summary("hidden_weights", W)
+    #   b = tf.Variable(tf.zeros([self.n_hidden[0]]), name="bias")
+    #   tf.histogram_summary("hidden_bias", b)
+    #
+    # with tf.variable_scope('output', reuse=None):
+    #   w_out = tf.get_variable("weights", shape=[self.n_hidden[0], self.n_classes], initializer=self.weight_initializer, regularizer=self.weight_regularizer)
+    #   tf.histogram_summary("output_weights", w_out)
+    #   b_out = tf.Variable(tf.zeros([self.n_classes]), name="bias")
+    #   tf.histogram_summary("output_bias", b_out)
+
+    # with tf.variable_scope('hidden', reuse=None):
+    #   W = tf.get_variable("weights", shape=[x.get_shape()[1], self.n_hidden[0]], initializer=tf.random_normal_initializer(mean=0.0, stddev=1e-2), regularizer=self.weight_regularizer)
+    #   tf.histogram_summary("hidden_weights", W)
+    #   b = tf.Variable(tf.zeros([self.n_hidden[0]]), name="bias")
+    #   tf.histogram_summary("hidden_bias", b)
+    #
+    # with tf.variable_scope('output', reuse=None):
+    #   w_out = tf.get_variable("weights", shape=[self.n_hidden[0], self.n_classes], initializer=tf.random_normal_initializer(mean=0.0, stddev=1e-2), regularizer=self.weight_regularizer)
+    #   tf.histogram_summary("output_weights", w_out)
+    #   b_out = tf.Variable(tf.zeros([self.n_classes]), name="bias")
+    #   tf.histogram_summary("output_bias", b_out)
+
     with tf.variable_scope('hidden', reuse=None):
-      W = tf.get_variable("weights", shape=[x.get_shape()[1], self.n_hidden[0]], initializer=self.weight_initializer, regularizer=self.weight_regularizer)
[…]

### 2016-11-22 practical_2/train_mlp.py

@@ -100,18 +100,39 @@ def train():
 
   model = MLP()
   x_ = model.inference(x)
-  loss = model.loss(x_, y_)
-  accuracy = model.accuracy(x_, y_)
-  train_step = tf.train.GradientDescentOptimizer(LEARNING_RATE_DEFAULT).minimize(loss)
+  with tf.name_scope('loss'):
+    loss = model.loss(x_, y_)
+  with tf.name_scope('accuracy'):
+    accuracy = model.accuracy(x_, y_)
+  with tf.name_scope('train_step'):
+    train_step = tf.train.GradientDescentOptimizer(LEARNING_RATE_DEFAULT).minimize(loss)
+
 
   init = tf.initialize_all_variables()
   sess = tf.Session()
   sess.run(init)
 
-  for _ in range(MAX_STEPS_DEFAULT):
+  tf.scalar_summary('accuracy', accuracy)
+  tf.scalar_summary('loss', loss)
+  tf.histogram_summary("logits", x_)
+  merged = tf.merge_all_summaries()
+
+
+  train_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/train', sess.graph)
+  test_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/test', sess.graph)
+
+  for i in range(1, MAX_STEPS_DEFAULT+1):
       batch_xs, batch_ys = cifar10.train.next_batch(BATCH_SIZE_DEFAULT)
-      i, l, acc = sess.run([train_step, loss, accuracy], feed_dict={x: batch_xs, y_: batch_ys})
-      # print(l, acc)
+      __, Summary, l, acc = sess.run([train_step, merged, loss, accuracy], feed_dict={x: batch_xs, y_: batch_ys})
+      train_writer.add_summary(Summary, i)
+
+      if i % 100 == 0.0:
+          batch_xs, batch_ys = cifar10.test.images, cifar10.test.labels
+          __, Summary, l, acc = sess.run([train_step, merged, loss, accuracy], feed_dict={x: batch_xs, y_: batch_ys})
+          test_writer.add_summary(Summary, i)
+
+
+  train_writer.close()
 
   #######################
   # END OF YOUR CODE    #

### 2016-11-22 practical_2/report/report_lastname.tex
update

@@
 \begin{enumerate}
-\item 
+\item TensorFlow \emph{variables} are stored structures containing tensors, \emph{constants} are constant variables in Tensorflow, \emph{placeholders} are used in the place of variables at graph initialization when there are no variables.
+The differences are that constants cannot change their values in contrast with variables, and that placeholder are replacing variables at initialization phase.
 \item There are two ways to declare variable in TensorFlow:
@@
 \item
-\item
-\item
-\item
+\item A computational \emph{graph}, \emph{tensors} for the variables and \emph{operator}.
+\item In variable scopes, variables can be created, adopting the prefix of the scope in their name, variable scopes enable variable sharing in different places in the code.
+The differences between name scopes and variable scopes is in the former creates an hierarchy for operations and variables in the graph, while the latter helps mostly in variable sharing.
+\item You can freeze a variable tensor during training by setting \texttt{trainable=True} upon creating the variable, this way it will not get updated during optimization.
 \item

### 2016-11-22 practical_2/report/report_methenitis.tex
update

--- 2016-11-22 practical_2/report/report_lastname.tex
@@
 In this assignment I got familiar with TensorFlow. I created a single hidden layer network with ReLU activation function to learn features for the CIFAR10 dataset.
+The accuracy obtained in the test set, $0.46$, is similar to the neural network model of the previous assignment. 
 \end{abstract}
@@
 \item You can freeze a variable tensor during training by setting \texttt{trainable=True} upon creating the variable, this way it will not get updated during optimization.
-\item
-\item
+\item Yes Tensorflow uses automatic differentiation, while this can be a disadvantage for higher numbers of hidden layer due to dependencies.
+The advantages are obvious, there is no need to compute difficult derivatives of high complexity.
+\item One way is like the assignment, reading using a python script the data for every train step and feeding the data in the graph.
+The other way is to read all the data from csv files at the beginning.
 \end{enumerate}
@@
 Figure~\ref{fig:acclosstrain} presents the accuracy and the loss in the training set recorded for every epoch.
-
+The accuracy is higher than $0.45$ similar to the performance in the training set of the previous assignment, while the loss converges close to zero after 500 epochs.
 \begin{figure}
@@
 \end{figure}
-
-Figure~\ref{fig:acclosstest} presents the accuracy and the loss in the test set recorded for every 100-epochs.
+Figure~\ref{fig:acclosstest} presents the accuracy and the loss in the test set recorded every 100-epochs.
+As you can see the accuracy drops after 1200 epochs, the model is overfitting.
 
@@
 Figure~\ref{fig:graph} presents the graph of the created model as this is illustrated by TensorBoard.
+Using different namespaces where necessary we can illustrate the structure of the model.
+You can see the two placeholder, one given as input to the relu layer and the second as the output of the linear layer, also connected to the accuracy module.
+The two layer are connected to the loss module that then updates all weights in the output and hidden layers.
 
@@
 Figure~\ref{fig:histogramlogits} presents the histogram of the logits.
+We can observe that only the variance of the logits change.
 
@@
 \section{Conclusion}
-Should contain conclusion of this study.
-For example, you can try to answer the following questions.
-What was done during this assignment? What features of TensorBoard were positive and what were negative for implementing MLP model and performing the experiments?
-What are the main insights you got from the study of the MLP model on CIFAR10 dataset?
+Although I did not have time to finish all the questions in the assignment I found it very useful.
+Tensorflow provides an easy to use library to create and train models and visualize everything is happening during the training of the model.
 

### 2016-11-29 practical_2/report/report_methenitis.tex
initial commit ass 3

@@
 In this assignment I got familiar with TensorFlow. I created a single hidden layer network with ReLU activation function to learn features for the CIFAR10 dataset.
-The accuracy obtained in the test set, $0.46$, is similar to the neural network model of the previous assignment. 
+Similarly to the previous assignment, the accuracy obtained in the test set was approximately $0.46$.
 \end{abstract}
@@
 The differences are that constants cannot change their values in contrast with variables, and that placeholder are replacing variables at initialization phase.
+In the context of convolutional neural networks constants can be the convolution filters, tensor for the input pixel values, and placeholder for initializing the pixel input space.
 \item There are two ways to declare variable in TensorFlow:
@@
 \item You can freeze a variable tensor during training by setting \texttt{trainable=True} upon creating the variable, this way it will not get updated during optimization.
-\item Yes Tensorflow uses automatic differentiation, while this can be a disadvantage for higher numbers of hidden layer due to dependencies.
-The advantages are obvious, there is no need to compute difficult derivatives of high complexity.
+\item Yes Tensorflow uses automatic differentiation.
+The advantages are obvious, there is no need to compute difficult derivatives of high complexity, while this can be a disadvantage for large numbers of hidden layers due to dependencies to compute the derivatives.
 \item One way is like the assignment, reading using a python script the data for every train step and feeding the data in the graph.
-The other way is to read all the data from csv files at the beginning.
+The other way is to read all the data from files at the beginning.
 \end{enumerate}
@@
 Although I did not have time to finish all the questions in the assignment I found it very useful.
-Tensorflow provides an easy to use library to create and train models and visualize everything is happening during the training of the model.
+Tensorflow provides an easy to use library to create and train models, visualizing everything is happening during the training of the model.
 

### 2016-12-01 practical_3/convnet.py
update

@@ -3,7 +3,9 @@ from __future__ import division
 from __future__ import print_function
 
 import tensorflow as tf
+from tensorflow.contrib.layers import regularizers
 import numpy as np
+from tensorflow.models.image.cifar10 import cifar10
 
 
 
@@ -55,11 +57,67 @@ class ConvNet(object):
             ########################
             # PUT YOUR CODE HERE  #
             ########################
-            raise NotImplementedError
+            with tf.variable_scope('conv1') as scope:
+                W_conv1 = tf.get_variable('weights', shape=[5, 5, 3, 64],
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.1),
+                                          regularizer=regularizers.l2_regularizer(0.001))
+                b_conv1 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
+
+            h_conv1 = tf.nn.relu(tf.nn.conv2d(x, W_conv1, strides=[1, 1, 1, 1], padding='SAME') + b_conv1)
+            h_pool1 = tf.nn.max_pool(h_conv1, ksize=[1, 3, 3, 1], strides=[1, 2, 2, 1], padding='SAME')
+
+            print(h_pool1.get_shape())
+
+            with tf.variable_scope('conv2') as scope:
+                W_conv2 = tf.get_variable('weights', shape=[5, 5, 64, 64],
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.1),
+                                          regularizer=regularizers.l2_regularizer(0.001))
+                b_conv2 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
+
+            h_conv2 = tf.nn.relu(tf.nn.conv2d(h_pool1, W_conv2, strides=[1, 1, 1, 1], padding='SAME') + b_conv2)
+            h_pool2 = tf.nn.max_pool(h_conv2, ksize=[1, 3, 3, 1], strides=[1, 2, 2, 1], padding='SAME')
+
+            print(h_pool2.get_shape())
+
+            with tf.variable_scope('flatten') as scope:
+                flatten = tf.reshape(h_pool2, [128, -1])
+
+            with tf.variable_scope('fc1') as scope:
+                W_fc1 = tf.get_variable('weights',
+                                        shape=[128, 384],
+                                        initializer=tf.random_normal_initializer(mean=0.0, stddev=0.1),
+                                        regularizer=regularizers.l2_regularizer(0.001))
[…]

### 2016-12-01 practical_3/train_model.py

@@ -7,6 +7,9 @@ import os
 
 import tensorflow as tf
 import numpy as np
+from convnet import ConvNet
+
+import cifar10_utils
 
 LEARNING_RATE_DEFAULT = 1e-4
 BATCH_SIZE_DEFAULT = 128
@@ -19,6 +22,8 @@ OPTIMIZER_DEFAULT = 'ADAM'
 DATA_DIR_DEFAULT = './cifar10/cifar-10-batches-py'
 LOG_DIR_DEFAULT = './logs/cifar10'
 CHECKPOINT_DIR_DEFAULT = './checkpoints'
+
+cifar10 = cifar10_utils.get_cifar10(DATA_DIR_DEFAULT)
 
 def train_step(loss):
     """
@@ -80,7 +85,44 @@ def train():
     ########################
     # PUT YOUR CODE HERE  #
     ########################
-    raise NotImplementedError
+    model = ConvNet()
+
+    x = tf.placeholder(tf.float32, shape=[None, 32, 32, 3])
+    y_ = tf.placeholder(tf.float32, shape=[None, 10])
+
+    x_ = model.inference(x)
+
+    with tf.name_scope('loss'):
+        loss = model.loss(x_, y_)
+
+    with tf.name_scope('accuracy'):
+        accuracy = model.accuracy(x_, y_)
+
+    with tf.name_scope('train'):
+        train_step = tf.train.GradientDescentOptimizer(LEARNING_RATE_DEFAULT).minimize(loss)
+
+    init = tf.initialize_all_variables()
+    session = tf.Session()
+    session.run(init)
+
+    tf.scalar_summary('accuracy', accuracy)
+    tf.scalar_summary('loss', loss)
+    tf.histogram_summary('logits', x_)
+    merged = tf.merge_all_summaries()
+
+    train_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/train', session.graph)
+    test_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/test', session.graph)
+
+    for iteration in range(1, MAX_STEPS_DEFAULT+1):
+        batch_x, batch_y = cifar10.train.next_batch(BATCH_SIZE_DEFAULT)
+        __, summary, l, acc = session.run([train_step, merged, loss, accuracy], feed_dict={x:batch_x, y_:batch_y})
+        train_writer.add_summary(summary, iteration)
+
+        if iteration % EVAL_FREQ_DEFAULT == 0.0:
[…]

### 2016-12-01 practical_3/convnet.py
update

@@ -59,45 +59,35 @@ class ConvNet(object):
             ########################
             with tf.variable_scope('conv1') as scope:
                 W_conv1 = tf.get_variable('weights', shape=[5, 5, 3, 64],
-                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.1),
-                                          regularizer=regularizers.l2_regularizer(0.001))
+                                      initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
                 b_conv1 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
 
             h_conv1 = tf.nn.relu(tf.nn.conv2d(x, W_conv1, strides=[1, 1, 1, 1], padding='SAME') + b_conv1)
             h_pool1 = tf.nn.max_pool(h_conv1, ksize=[1, 3, 3, 1], strides=[1, 2, 2, 1], padding='SAME')
 
-            print(h_pool1.get_shape())
-
             with tf.variable_scope('conv2') as scope:
                 W_conv2 = tf.get_variable('weights', shape=[5, 5, 64, 64],
-                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.1),
-                                          regularizer=regularizers.l2_regularizer(0.001))
+                                      initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
                 b_conv2 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
 
             h_conv2 = tf.nn.relu(tf.nn.conv2d(h_pool1, W_conv2, strides=[1, 1, 1, 1], padding='SAME') + b_conv2)
             h_pool2 = tf.nn.max_pool(h_conv2, ksize=[1, 3, 3, 1], strides=[1, 2, 2, 1], padding='SAME')
 
-            print(h_pool2.get_shape())
-
             with tf.variable_scope('flatten') as scope:
-                flatten = tf.reshape(h_pool2, [128, -1])
+                flatten = tf.reshape(h_pool2, shape=[-1, int(h_pool2.get_shape()[1]*h_pool2.get_shape()[2]*h_pool2.get_shape()[3])])
 
             with tf.variable_scope('fc1') as scope:
                 W_fc1 = tf.get_variable('weights',
-                                        shape=[128, 384],
-                                        initializer=tf.random_normal_initializer(mean=0.0, stddev=0.1),
-                                        regularizer=regularizers.l2_regularizer(0.001))
[…]

### 2016-12-01 practical_3/train_model.py

@@ -12,7 +12,7 @@ from convnet import ConvNet
 import cifar10_utils
 
 LEARNING_RATE_DEFAULT = 1e-4
-BATCH_SIZE_DEFAULT = 128
+BATCH_SIZE_DEFAULT = 64
 MAX_STEPS_DEFAULT = 15000
 EVAL_FREQ_DEFAULT = 1000
 CHECKPOINT_FREQ_DEFAULT = 5000
@@ -99,7 +99,7 @@ def train():
         accuracy = model.accuracy(x_, y_)
 
     with tf.name_scope('train'):
-        train_step = tf.train.GradientDescentOptimizer(LEARNING_RATE_DEFAULT).minimize(loss)
+        train_step = tf.train.AdamOptimizer(LEARNING_RATE_DEFAULT).minimize(loss)
 
     init = tf.initialize_all_variables()
     session = tf.Session()
@@ -118,9 +118,19 @@ def train():
         __, summary, l, acc = session.run([train_step, merged, loss, accuracy], feed_dict={x:batch_x, y_:batch_y})
         train_writer.add_summary(summary, iteration)
 
-        if iteration % EVAL_FREQ_DEFAULT == 0.0:
-            batch_x, batch_y = cifar10.test.images, cifar10.test.labels
-            __, summary, l, acc = session.run([train_step, merged, loss, accuracy], feed_dict={x: batch_x, y_: batch_y})
+        if iteration % 1000 == 0.0:
+            _split  = 250
+            avg_loss, avg_acc = 0.0, 0.0
+            for _iter in range(int(len(cifar10.test.images) / _split)):
+                batch_x, batch_y = cifar10.test.images[_iter * _split:((_iter + 1) * _split)],\
+                                   cifar10.test.labels[_iter * _split:((_iter + 1) * _split)]
+
+                __, summary, l, acc = session.run([train_step, merged, loss, accuracy], feed_dict={x: batch_x, y_: batch_y})
+                avg_loss += l
+                avg_acc += acc
+            avg_loss /= float(len(cifar10.test.images) / _split)
+            avg_acc /= float(len(cifar10.test.images) / _split)
+            print(iteration, avg_loss, avg_acc)
             test_writer.add_summary(summary, iteration)
 
     ########################

### 2016-12-01 practical_3/train_model.py
update

@@ -12,7 +12,7 @@ from convnet import ConvNet
 import cifar10_utils
 
 LEARNING_RATE_DEFAULT = 1e-4
-BATCH_SIZE_DEFAULT = 64
+BATCH_SIZE_DEFAULT = 128
 MAX_STEPS_DEFAULT = 15000
 EVAL_FREQ_DEFAULT = 1000
 CHECKPOINT_FREQ_DEFAULT = 5000

### 2016-12-05 practical_3/report/report_methenitis.tex
update

--- 2016-11-22 practical_2/report/report_lastname.tex
@@
 \usepackage{microtype}      % microtypography
-\usepackage{fancyvrb,xcolor}
 \usepackage{graphicx}
@@
 \author{
-  Georgios Methenitis \\
-  \texttt{georgios.methenitis@cwi.nl}
+  David S.~Hippocampus \\
+  \texttt{hippo@cs.cranberry-lemon.edu}
 }
@@
 \begin{abstract}
-In this assignment I got familiar with TensorFlow. I created a single hidden layer network with ReLU activation function to learn features for the CIFAR10 dataset.
+Should contain information about the current task and the summary of the study of the CNN models on CIFAR10 dataset.
+
 \end{abstract}
@@
 \section{Task 1}
-\begin{enumerate}
-\item 
-\item There are two ways to declare variable in TensorFlow:
-\begin{itemize}
-\item \begin{small}
-\begin{verbatim}
-var = tf.get_variable("var_name", shape=[..., ...])
-\end{verbatim}
-\end{small}
-\item \begin{small}
-\begin{verbatim}
-var = tf.Variable(tf.zeros([..., ...]), name="var_name")
-\end{verbatim}
-\end{small}
-\end{itemize}
+Should contain all needed information about Task 1 and report of all your experiments for that task.
 
-\item The command \texttt{tf.shape(x)} returns the shape of the input of tensor \texttt{x} in an 1-D vector, while \texttt{x.get\_shape()} return the size of the tensor.
-\item
-\item
-\item
-\item
-\item
-\item
-\item
-\end{enumerate}
+Figure~\ref{fig:1}, \ref{fig:2}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[height=3.2cm]{acc1.png}\	
+\includegraphics[height=3.2cm]{loss1.png}
+\caption{Accuracy (left) and loss on the training set with batch size of $128$ samples. The accuracy approximates $1.0$ in the training set implying that the model overfits the training set.}
+\label{fig:1}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[height=3.2cm]{acc2.png}\	
+\includegraphics[height=3.2cm]{loss2.png}
+\caption{Accuracy (left) and loss on the test set with batch size of $128$ samples. The accuracy is $0.88$ after $15000$ steps.}
+\label{fig:2}
+\end{figure}
+
+\subsection{Smaller batch size}
+
+Figure~\ref{fig:3}, \ref{fig:4}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[height=3.2cm]{acc3.png}\	
+\includegraphics[height=3.2cm]{loss3.png}
+\caption{Accuracy (left) and loss on the training set with batch size of $128$ samples. The accuracy approximates $1.0$ in the training set implying that the model overfits the training set.}
+\label{fig:3}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[height=3.2cm]{acc4.png}\	
+\includegraphics[height=3.2cm]{loss4.png}
+\caption{Accuracy (left) and loss on the test set with batch size of $128$ samples. The accuracy is $0.88$ after $15000$ steps.}
+\label{fig:4}
+\end{figure}
 
 \section{Task 2}
-In this task I implemented the following functions in \texttt{mlp.py}, more specifically the \texttt{inference}, \texttt{loss}, and \texttt{accuracy}.
+Should contain all needed information about Task 2 and report of all your experiments for that task.
 
-\begin{small}
-\begin{verbatim}
-  def inference(self, x):
-    with tf.variable_scope('hidden', reuse=None):
-      W = tf.get_variable("weights", shape=[x.get_shape()[1], self.n_hidden[0]],
-       initializer=self.weight_initializer, regularizer=self.weight_regularizer)
-      tf.histogram_summary("hidden_weights", W)
-      b = tf.Variable(tf.zeros([self.n_hidden[0]]), name="bias")
-      tf.histogram_summary("hidden_bias", b)
-
-    with tf.variable_scope('output', reuse=None):
-      w_out = tf.get_variable("weights", shape=[self.n_hidden[0], self.n_classes],
-       initializer=self.weight_initializer, regularizer=self.weight_regularizer)
-      tf.histogram_summary("output_weights", w_out)
-      b_out = tf.Variable(tf.zeros([self.n_classes]), name="bias")
-      tf.histogram_summary("output_bias", b_out)
-
-    with tf.name_scope('relu_layer'):
-      input = self.activation_fn(tf.matmul(x, W) + b)
-    with tf.name_scope('linear_layer'):
-      output = tf.matmul(input, w_out) + b_out
-
-    return output
-
-  def loss(self, logits, labels):
-
-    loss = tf.reduce_mean(tf.nn.softmax_cross_entropy_with_logits(logits, labels, name=None))
-    with tf.variable_scope("hidden", reuse=True):
-      loss += 0.5 * tf.reduce_sum(tf.get_variable("weights")**2)
-    with tf.variable_scope("output", reuse=True):
-      loss += 0.5 * tf.reduce_sum(tf.get_variable("weights")**2)
-
-    return loss
-
-  def accuracy(self, logits, labels):
-    correct_prediction = tf.equal(tf.argmax(labels, 1), tf.argmax(logits, 1))
-    accuracy = tf.reduce_mean(tf.cast(correct_prediction, tf.float32))
-    return accuracy
-\end{verbatim}
-\end{small}
-I also implemented the function \texttt{train} in the file \texttt{train\_mlp.py}:
-\begin{small}
-\begin{verbatim}
-def train():
-  # placeholder for input and output tensors allowing to create operations and the computation graph
-  x = tf.placeholder(tf.float32, shape=[None, 3072])
-  y_ = tf.placeholder(tf.float32, shape=[None, 10])
-
-  # model, namescopes for summary
-  model = MLP()
-  x_ = model.inference(x)
-  with tf.name_scope('loss'):
-    loss = model.loss(x_, y_)
-  with tf.name_scope('accuracy'):
-    accuracy = model.accuracy(x_, y_)
-  with tf.name_scope('train_step'):
-    train_step = tf.train.GradientDescentOptimizer(LEARNING_RATE_DEFAULT).minimize(loss)
-
-  # session
-  init = tf.initialize_all_variables()
-  sess = tf.Session()
-  sess.run(init)
-
-  # merged summary for the graph, the loss and accuracy
-  tf.scalar_summary('accuracy', accuracy)
-  tf.scalar_summary('loss', loss)
-  tf.histogram_summary("logits", x_) # logits histogram
-  merged = tf.merge_all_summaries()
-
-  train_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/train', sess.graph)
-  test_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/test', sess.graph)
-
-  for i in range(1, MAX_STEPS_DEFAULT+1):
-      batch_xs, batch_ys = cifar10.train.next_batch(BATCH_SIZE_DEFAULT)
-      __, Summary, l, acc = sess.run([train_step, merged, loss, accuracy],
-      feed_dict={x: batch_xs, y_: batch_ys})
-      train_writer.add_summary(Summary, i)
-
-      if i % 100 == 0.0:
-          batch_xs, batch_ys = cifar10.test.images, cifar10.test.labels
-          __, Summary, l, acc = sess.run([train_step, merged, loss, accuracy],
-           feed_dict={x: batch_xs, y_: batch_ys})
-          test_writer.add_summary(Summary, i)
-
-  train_writer.close()
-\end{verbatim}
-\end{small}
-
-Figure~\ref{fig:acclosstrain} presents the accuracy and the loss in the training set recorded for every epoch.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{loss.png}\	
-\includegraphics[width=0.45\textwidth]{accuracy.png}
-\caption{Recorded accuracy and loss for the training set.}
-\label{fig:acclosstrain}
-\end{figure}
-
-Figure~\ref{fig:acclosstest} presents the accuracy and the loss in the test set recorded for every 100-epochs.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{accuracy_t.png}\	
-\includegraphics[width=0.45\textwidth]{loss_t.png}
-\caption{Recorded accuracy and loss for the test set.}
-\label{fig:acclosstest}
-\end{figure}
-
-Figure~\ref{fig:graph} presents the graph of the created model as this is illustrated by TensorBoard.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.9\textwidth]{graph.png}
-\caption{Graph of the model.}
-\label{fig:graph}
-\end{figure}
-
-Figure~\ref{fig:histogramsunits} presents the histograms of the weights and the biases in every unit of the model, in the hidden and the output units respectively.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{hidden_weights.png}
-\includegraphics[width=0.3\textwidth]{hidden_bias.png}
-\includegraphics[width=0.3\textwidth]{output_weights.png}
-\includegraphics[width=0.3\textwidth]{output_bias.png}
-\caption{Histograms of weights and bias in the hidden layer, and weights and bias in the output linear layer.}
-\label{fig:histogramsunits}
-\end{figure}
-
-Figure~\ref{fig:histogramlogits} presents the histogram of the logits.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.4\textwidth]{logits.png}
-\caption{Histograms of logits.}
-\label{fig:histogramlogits}
-\end{figure}
+\section{Task 3}
+Should contain all needed information about Task 3 and report of all your experiments for that task.
 
@@
 Should contain conclusion of this study.
-For example, you can try to answer the following questions.
-What was done during this assignment? What features of TensorBoard were positive and what were negative for implementing MLP model and performing the experiments?
-What are the main insights you got from the study of the MLP model on CIFAR10 dataset?
+
+%\section*{References}
+%
+%\small
+%
+%[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
+%for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
+%T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
+%  Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.
+%
+%[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
+%  Exploring Realistic Neural Models with the GEneral NEural SImulation
+%  System.}  New York: TELOS/Springer--Verlag.
+%
+%[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
+%learning and recall at excitatory recurrent synapses and cholinergic
+%modulation in rat hippocampal region CA3. {\it Journal of
+%  Neuroscience} {\bf 15}(7):5249-5262.
 

### 2016-12-05 practical_3/convnet.py

@@ -3,11 +3,6 @@ from __future__ import division
 from __future__ import print_function
 
 import tensorflow as tf
-from tensorflow.contrib.layers import regularizers
-import numpy as np
-from tensorflow.models.image.cifar10 import cifar10
-
-
 
 class ConvNet(object):
     """
@@ -58,48 +53,59 @@ class ConvNet(object):
             # PUT YOUR CODE HERE  #
             ########################
             with tf.variable_scope('conv1') as scope:
-                W_conv1 = tf.get_variable('weights', shape=[5, 5, 3, 64],
-                                      initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+                w_conv1 = tf.get_variable('weights',
+                                          shape=[5, 5, 3, 64],
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+
                 b_conv1 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
 
-            h_conv1 = tf.nn.relu(tf.nn.conv2d(x, W_conv1, strides=[1, 1, 1, 1], padding='SAME') + b_conv1)
-            h_pool1 = tf.nn.max_pool(h_conv1, ksize=[1, 3, 3, 1], strides=[1, 2, 2, 1], padding='SAME')
+                h_conv1 = tf.nn.relu(tf.nn.conv2d(x, w_conv1, strides=[1, 1, 1, 1], padding='SAME') + b_conv1)
+
+                h_pool1 = tf.nn.max_pool(h_conv1, ksize=[1, 3, 3, 1], strides=[1, 2, 2, 1], padding='SAME', name="h_f_1")
 
             with tf.variable_scope('conv2') as scope:
-                W_conv2 = tf.get_variable('weights', shape=[5, 5, 64, 64],
-                                      initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+                w_conv2 = tf.get_variable('weights',
+                                          shape=[5, 5, 64, 64],
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+
                 b_conv2 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
 
-            h_conv2 = tf.nn.relu(tf.nn.conv2d(h_pool1, W_conv2, strides=[1, 1, 1, 1], padding='SAME') + b_conv2)
[…]

### 2016-12-05 practical_3/train_model.py

@@ -12,7 +12,7 @@ from convnet import ConvNet
 import cifar10_utils
 
 LEARNING_RATE_DEFAULT = 1e-4
-BATCH_SIZE_DEFAULT = 128
+BATCH_SIZE_DEFAULT = 64
 MAX_STEPS_DEFAULT = 15000
 EVAL_FREQ_DEFAULT = 1000
 CHECKPOINT_FREQ_DEFAULT = 5000
@@ -113,13 +113,18 @@ def train():
     train_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/train', session.graph)
     test_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/test', session.graph)
 
+    saver = tf.train.Saver(tf.all_variables())
+
     for iteration in range(1, MAX_STEPS_DEFAULT+1):
         batch_x, batch_y = cifar10.train.next_batch(BATCH_SIZE_DEFAULT)
         __, summary, l, acc = session.run([train_step, merged, loss, accuracy], feed_dict={x:batch_x, y_:batch_y})
         train_writer.add_summary(summary, iteration)
 
+        if iteration % CHECKPOINT_FREQ_DEFAULT == 0:
+            saver.save(session, CHECKPOINT_DIR_DEFAULT + "/model-at-" + str(iteration) + ".ckpt")
+
         if iteration % 1000 == 0.0:
-            _split  = 250
+            _split = 250
             avg_loss, avg_acc = 0.0, 0.0
             for _iter in range(int(len(cifar10.test.images) / _split)):
                 batch_x, batch_y = cifar10.test.images[_iter * _split:((_iter + 1) * _split)],\
@@ -132,7 +137,6 @@ def train():
             avg_acc /= float(len(cifar10.test.images) / _split)
             print(iteration, avg_loss, avg_acc)
             test_writer.add_summary(summary, iteration)
-
     ########################
     # END OF YOUR CODE    #
     ########################
@@ -179,7 +183,59 @@ def train_siamese():
     ########################
     # PUT YOUR CODE HERE  #
     ########################
-    raise NotImplementedError
+    model = ConvNet()
+
+    x = tf.placeholder(tf.float32, shape=[None, 32, 32, 3])
+    y_ = tf.placeholder(tf.float32, shape=[None, 10])
+
+    x_ = model.inference(x)
+
+    with tf.name_scope('loss'):
+        loss = model.loss(x_, y_)
+
[…]

### 2016-12-05 practical_3/cifar10_siamese_utils.py
update

@@ -119,7 +119,8 @@ def dense_to_one_hot(labels_dense, num_classes):
   labels_one_hot.flat[index_offset + labels_dense.ravel()] = 1
   return labels_one_hot
 
-def create_dataset(source='Train', num_tuples = 500, batch_size = 128, fraction_same = 0.2):
+
+def create_dataset(source_data, num_tuples = 500, batch_size = 128, fraction_same = 0.2):
     """
     Creates a list of validation tuples. A tuple consist of image pairs and a label.
     A tuple is basically a minibatch to be used in validation.
@@ -143,7 +144,7 @@ def create_dataset(source='Train', num_tuples = 500, batch_size = 128, fraction_
     The ratio between the number of + and - cases is controlled by fraction_same.
 
     Args:
-      source: Where to sample from train or test set.
+      source_data: Subset of CIFAR10 data to sample from. You can use validation split here.
       num_tuples: Number of tuples to be used in the validation
       batch_size: Batch size.
       fraction_same: float in range [0,1], defines the fraction
@@ -156,7 +157,7 @@ def create_dataset(source='Train', num_tuples = 500, batch_size = 128, fraction_
     ########################
     # PUT YOUR CODE HERE  #
     ########################
-    raise NotImplementedError
+    print(source_data.train._images.shape)
     ########################
     # END OF YOUR CODE    #
     ########################

### 2016-12-05 practical_3/train_model.py

@@ -10,6 +10,7 @@ import numpy as np
 from convnet import ConvNet
 
 import cifar10_utils
+import cifar10_siamese_utils
 
 LEARNING_RATE_DEFAULT = 1e-4
 BATCH_SIZE_DEFAULT = 64
@@ -24,6 +25,14 @@ LOG_DIR_DEFAULT = './logs/cifar10'
 CHECKPOINT_DIR_DEFAULT = './checkpoints'
 
 cifar10 = cifar10_utils.get_cifar10(DATA_DIR_DEFAULT)
+
+cifar10_siamese = cifar10_siamese_utils.get_cifar10(DATA_DIR_DEFAULT,
+                                                     one_hot=False)
+
+val_set = cifar10_siamese_utils.create_dataset(cifar10_siamese,
+                                               num_tuples=600,
+                                               batch_size=BATCH_SIZE_DEFAULT,
+                                               fraction_same=0.2)
 
 def train_step(loss):
     """
@@ -183,59 +192,7 @@ def train_siamese():
     ########################
     # PUT YOUR CODE HERE  #
     ########################
-    model = ConvNet()
-
-    x = tf.placeholder(tf.float32, shape=[None, 32, 32, 3])
-    y_ = tf.placeholder(tf.float32, shape=[None, 10])
-
-    x_ = model.inference(x)
-
-    with tf.name_scope('loss'):
-        loss = model.loss(x_, y_)
-
-    with tf.name_scope('accuracy'):
-        accuracy = model.accuracy(x_, y_)
-
-    with tf.name_scope('train'):
-        train_step = tf.train.AdamOptimizer(LEARNING_RATE_DEFAULT).minimize(loss)
-
-    init = tf.initialize_all_variables()
-    session = tf.Session()
-    session.run(init)
-
-    tf.scalar_summary('accuracy', accuracy)
-    tf.scalar_summary('loss', loss)
-    tf.histogram_summary('logits', x_)
-    merged = tf.merge_all_summaries()
-
-    train_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/train', session.graph)
-    test_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/test', session.graph)
-
-    saver = tf.train.Saver(tf.all_variables())
-
-    for iteration in range(1, MAX_STEPS_DEFAULT + 1):
-        batch_x, batch_y = cifar10.train.next_batch(BATCH_SIZE_DEFAULT)
[…]

### 2016-12-06 practical_3/cifar10_siamese_utils.py
update with siamese architecture

@@ -157,11 +157,25 @@ def create_dataset(source_data, num_tuples = 500, batch_size = 128, fraction_sam
     ########################
     # PUT YOUR CODE HERE  #
     ########################
-    print(source_data.train._images.shape)
+    dset = []
+    # for sample in range(num_tuples):
+    #   # number of correct images
+    #   n_correct = int(fraction_same * batch_size)
+    #   random_im = np.array(np.random.choice(range(source_data.train._images.shape[0]), replace=False, size=batch_size))
+    #
+    #   matches = [np.where(source_data.train._labels == source_data.train._labels[x]) for x in random_im]
+    #   mismatches = [np.where(source_data.train._labels != source_data.train._labels[x]) for x in random_im]
+    #
+    #   tuple = []
+    #   for i in range(0, n_correct):
+    #     tuple.append((random_im[i], np.random.choice(np.array(matches[i])[0]), 1))
+    #   for j in range(batch_size - n_correct, i, -1):
+    #     tuple.append((random_im[i], np.random.choice(np.array(mismatches[i])[0]), 0))
+    #   dset.append(tuple)
     ########################
     # END OF YOUR CODE    #
     ########################
-    return dset
+    return np.array(dset)
 
 class DataSet(object):
   """
@@ -237,7 +251,14 @@ class DataSet(object):
     ########################
     # PUT YOUR CODE HERE  #
     ########################
-    raise NotImplementedError
+    n_correct = int(fraction_same * batch_size)
+    random_index = np.array(np.random.choice(range(self._images.shape[0]), replace=False, size=batch_size))
+    matches = [np.random.choice(np.array(np.where(self._labels == self._labels[x]))[0]) for x in random_index]
+    mismatches = [np.random.choice(np.array(np.where(self._labels != self._labels[x]))[0]) for x in random_index]
+    x1 = self._images[random_index]
+    x2 = self._images[matches[:n_correct]]
+    x2 = np.vstack((x2, self._images[mismatches[n_correct:]]))
+    labels = np.hstack((np.ones((n_correct)), np.zeros((batch_size-n_correct))))
     ########################
     # END OF YOUR CODE    #
     ########################

### 2016-12-06 practical_3/convnet.py

@@ -105,12 +105,12 @@ class ConvNet(object):
 
                 b_fc3 = tf.Variable(tf.constant(0.0, shape=[10]), name='biases')
 
-            h_fc3 = tf.matmul(h_fc2, w_fc3) + b_fc3
+            logits = tf.matmul(h_fc2, w_fc3) + b_fc3
 
             ########################
             # END OF YOUR CODE    #
             ########################
-        return h_fc3
+        return logits
 
     def accuracy(self, logits, labels):
         """

### 2016-12-06 practical_3/siamese.py

@@ -45,7 +45,53 @@ class Siamese(object):
             ########################
             # PUT YOUR CODE HERE  #
             ########################
-            raise NotImplementedError
+            with tf.variable_scope('conv1', reuse=reuse) as scope:
+                w_conv1 = tf.get_variable('weights',
+                                          shape=[5, 5, 3, 64],
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+
+                b_conv1 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
+
+                h_conv1 = tf.nn.relu(tf.nn.conv2d(x, w_conv1, strides=[1, 1, 1, 1], padding='SAME') + b_conv1)
+
+                h_pool1 = tf.nn.max_pool(h_conv1, ksize=[1, 3, 3, 1], strides=[1, 2, 2, 1], padding='SAME', name="h_f_1")
+
+            with tf.variable_scope('conv2', reuse=reuse) as scope:
+                w_conv2 = tf.get_variable('weights',
+                                          shape=[5, 5, 64, 64],
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+
+                b_conv2 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
+
+                h_conv2 = tf.nn.relu(tf.nn.conv2d(h_pool1, w_conv2, strides=[1, 1, 1, 1], padding='SAME') + b_conv2)
+
+                h_pool2 = tf.nn.max_pool(h_conv2, ksize=[1, 3, 3, 1], strides=[1, 2, 2, 1], padding='SAME', name="h_f_2")
+
+            with tf.variable_scope('flatten', reuse=reuse) as scope:
+                flatten = tf.reshape(h_pool2, shape=[-1,
+                                                     int(h_pool2.get_shape()[1] *
+                                                         h_pool2.get_shape()[2] *
+                                                         h_pool2.get_shape()[3])], name="h_f_flatten")
+
+            with tf.variable_scope('fc1', reuse=reuse) as scope:
+                w_fc1 = tf.get_variable('weights',
+                                        shape=[flatten.get_shape()[1], 384],
+                                        initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+
+                b_fc1 = tf.Variable(tf.constant(0.0, shape=[384]), name='biases')
+
[…]

### 2016-12-06 practical_3/train_model.py

@@ -8,6 +8,7 @@ import os
 import tensorflow as tf
 import numpy as np
 from convnet import ConvNet
+from siamese import Siamese
 
 import cifar10_utils
 import cifar10_siamese_utils
@@ -192,7 +193,31 @@ def train_siamese():
     ########################
     # PUT YOUR CODE HERE  #
     ########################
-    cifar10_siamese.train.next_batch(BATCH_SIZE_DEFAULT)
+    model = Siamese()
+
+    x1 = tf.placeholder(tf.float32, shape=[None, 32, 32, 3])
+    x2 = tf.placeholder(tf.float32, shape=[None, 32, 32, 3])
+    y_ = tf.placeholder(tf.float32, shape=[None,])
+
+    x1_ = model.inference(x1, reuse=None)
+    x2_ = model.inference(x2, reuse=True)
+
+    with tf.name_scope('loss'):
+        loss = model.loss(x1_, x2_, y_, 0.2)
+
+    with tf.name_scope('train'):
+        train_step = tf.train.AdamOptimizer(LEARNING_RATE_DEFAULT).minimize(loss)
+
+    init = tf.initialize_all_variables()
+    session = tf.Session()
+    session.run(init)
+
+    for iteration in range(1, MAX_STEPS_DEFAULT+1):
+        batch_x1, batch_x2, batch_labels = cifar10_siamese.train.next_batch(BATCH_SIZE_DEFAULT)
+        __, l = session.run([train_step, loss], feed_dict={x1:batch_x1, x2:batch_x2, y_:batch_labels})
+        print(l)
+
+
     ########################
     # END OF YOUR CODE    #
     ########################

### 2016-12-07 practical_3/cifar10_siamese_utils.py
update fixed train and val sets

@@ -158,24 +158,21 @@ def create_dataset(source_data, num_tuples = 500, batch_size = 128, fraction_sam
     # PUT YOUR CODE HERE  #
     ########################
     dset = []
-    # for sample in range(num_tuples):
-    #   # number of correct images
-    #   n_correct = int(fraction_same * batch_size)
-    #   random_im = np.array(np.random.choice(range(source_data.train._images.shape[0]), replace=False, size=batch_size))
-    #
-    #   matches = [np.where(source_data.train._labels == source_data.train._labels[x]) for x in random_im]
-    #   mismatches = [np.where(source_data.train._labels != source_data.train._labels[x]) for x in random_im]
-    #
-    #   tuple = []
-    #   for i in range(0, n_correct):
-    #     tuple.append((random_im[i], np.random.choice(np.array(matches[i])[0]), 1))
-    #   for j in range(batch_size - n_correct, i, -1):
-    #     tuple.append((random_im[i], np.random.choice(np.array(mismatches[i])[0]), 0))
-    #   dset.append(tuple)
+    for sample_tuple in range(num_tuples):
+      n_correct = int(fraction_same * batch_size)
+      random_index = np.array(np.random.choice(range(int(source_data.train._images.shape[0] * 0.8),
+                                                     source_data.train._images.shape[0]), replace=False, size=batch_size))
+      matches = [np.random.choice(np.array(np.where(source_data.train._labels == source_data.train._labels[x]))[0]) for x in random_index]
+      mismatches = [np.random.choice(np.array(np.where(source_data.train._labels != source_data.train._labels[x]))[0]) for x in random_index]
+      x1 = source_data.train._images[random_index]
+      x2 = source_data.train._images[matches[:n_correct]]
+      x2 = np.vstack((x2, source_data.train._images[mismatches[n_correct:]]))
+      labels = np.hstack((np.ones((n_correct)), np.zeros((batch_size - n_correct))))
+      dset.append((x1,x2,labels))
     ########################
     # END OF YOUR CODE    #
     ########################
-    return np.array(dset)
+    return dset
 
 class DataSet(object):
   """
@@ -252,7 +249,7 @@ class DataSet(object):
     # PUT YOUR CODE HERE  #
     ########################
     n_correct = int(fraction_same * batch_size)
-    random_index = np.array(np.random.choice(range(self._images.shape[0]), replace=False, size=batch_size))
[…]

### 2016-12-07 practical_3/train_model.py

@@ -14,7 +14,7 @@ import cifar10_utils
 import cifar10_siamese_utils
 
 LEARNING_RATE_DEFAULT = 1e-4
-BATCH_SIZE_DEFAULT = 64
+BATCH_SIZE_DEFAULT = 128
 MAX_STEPS_DEFAULT = 15000
 EVAL_FREQ_DEFAULT = 1000
 CHECKPOINT_FREQ_DEFAULT = 5000
@@ -29,11 +29,6 @@ cifar10 = cifar10_utils.get_cifar10(DATA_DIR_DEFAULT)
 
 cifar10_siamese = cifar10_siamese_utils.get_cifar10(DATA_DIR_DEFAULT,
                                                      one_hot=False)
-
-val_set = cifar10_siamese_utils.create_dataset(cifar10_siamese,
-                                               num_tuples=600,
-                                               batch_size=BATCH_SIZE_DEFAULT,
-                                               fraction_same=0.2)
 
 def train_step(loss):
     """
@@ -193,6 +188,12 @@ def train_siamese():
     ########################
     # PUT YOUR CODE HERE  #
     ########################
+
+    val_set = cifar10_siamese_utils.create_dataset(cifar10_siamese,
+                                                   num_tuples=600,
+                                                   batch_size=BATCH_SIZE_DEFAULT,
+                                                   fraction_same=0.2)
+
     model = Siamese()
 
     x1 = tf.placeholder(tf.float32, shape=[None, 32, 32, 3])
@@ -212,12 +213,31 @@ def train_siamese():
     session = tf.Session()
     session.run(init)
 
+    tf.scalar_summary('loss', loss)
+    merged = tf.merge_all_summaries()
+
+    train_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/train', session.graph)
+    test_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/test', session.graph)
+
+    saver = tf.train.Saver(tf.all_variables())
+
     for iteration in range(1, MAX_STEPS_DEFAULT+1):
         batch_x1, batch_x2, batch_labels = cifar10_siamese.train.next_batch(BATCH_SIZE_DEFAULT)
-        __, l = session.run([train_step, loss], feed_dict={x1:batch_x1, x2:batch_x2, y_:batch_labels})
-        print(l)
+        __, summary, l = session.run([train_step, merged, loss], feed_dict={x1:batch_x1, x2:batch_x2, y_:batch_labels})
 
[…]

### 2016-12-11 practical_3/cifar10_siamese_utils.py
fixed train batch

@@ -159,18 +159,41 @@ def create_dataset(source_data, num_tuples = 500, batch_size = 128, fraction_sam
     ########################
     dset = []
     for sample_tuple in range(num_tuples):
-      n_correct = int(fraction_same * batch_size)
-      random_index = np.array(np.random.choice(range(int(source_data.train._images.shape[0] * 0.8),
-                                                     source_data.train._images.shape[0]), replace=False, size=batch_size))
-      matches = [np.random.choice(np.array(np.where(source_data.train._labels == source_data.train._labels[x]))[0]) for x in random_index]
-      mismatches = [np.random.choice(np.array(np.where(source_data.train._labels != source_data.train._labels[x]))[0]) for x in random_index]
-      x1 = source_data.train._images[random_index]
-      x2 = source_data.train._images[matches[:n_correct]]
-      x2 = np.vstack((x2, source_data.train._images[mismatches[n_correct:]]))
-      labels = np.hstack((np.ones((n_correct)), np.zeros((batch_size - n_correct))))
-      dset.append((x1,x2,labels))
+      if 0:
+        n_correct = int(fraction_same * batch_size)
+        random_index = np.array(np.random.choice(range(int(source_data.train._images.shape[0] * 0.8),
+                                                       source_data.train._images.shape[0]), replace=False, size=batch_size))
+        matches = [np.random.choice(np.array(np.where(source_data.train._labels == source_data.train._labels[x]))[0]) for x in random_index]
+        mismatches = [np.random.choice(np.array(np.where(source_data.train._labels != source_data.train._labels[x]))[0]) for x in random_index]
+        x1 = source_data.train._images[random_index]
+        x2 = source_data.train._images[matches[:n_correct]]
+        x2 = np.vstack((x2, source_data.train._images[mismatches[n_correct:]]))
+        labels = np.hstack((np.ones((n_correct)), np.zeros((batch_size - n_correct))))
+        dset.append((x1, x2, labels))
+      else:
+        n_correct = int(fraction_same * batch_size)
+        val_set_indexes = range(int(source_data.train._images.shape[0] * 0.8), source_data.train._images.shape[0])
+
+        index_x1 = np.random.choice(val_set_indexes)
+        label_x1 = source_data.train._labels[index_x1]
+
+        index_x2_similar = np.random.choice(val_set_indexes[0] +
[…]

### 2016-12-11 practical_3/train_model.py

@@ -115,8 +115,8 @@ def train():
     tf.histogram_summary('logits', x_)
     merged = tf.merge_all_summaries()
 
-    train_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/train', session.graph)
-    test_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/test', session.graph)
+    train_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/linear-train', session.graph)
+    test_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/linear-test', session.graph)
 
     saver = tf.train.Saver(tf.all_variables())
 
@@ -126,9 +126,9 @@ def train():
         train_writer.add_summary(summary, iteration)
 
         if iteration % CHECKPOINT_FREQ_DEFAULT == 0:
-            saver.save(session, CHECKPOINT_DIR_DEFAULT + "/model-at-" + str(iteration) + ".ckpt")
+            saver.save(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(iteration) + ".ckpt")
 
-        if iteration % 1000 == 0.0:
+        if iteration % EVAL_FREQ_DEFAULT == 0.0:
             _split = 250
             avg_loss, avg_acc = 0.0, 0.0
             for _iter in range(int(len(cifar10.test.images) / _split)):
@@ -138,8 +138,8 @@ def train():
                 __, summary, l, acc = session.run([train_step, merged, loss, accuracy], feed_dict={x: batch_x, y_: batch_y})
                 avg_loss += l
                 avg_acc += acc
-            avg_loss /= float(len(cifar10.test.images) / _split)
-            avg_acc /= float(len(cifar10.test.images) / _split)
+            avg_loss /= float(len(cifar10.test.images)) / float(_split)
+            avg_acc /= float(len(cifar10.test.images)) / float(_split)
             print(iteration, avg_loss, avg_acc)
             test_writer.add_summary(summary, iteration)
     ########################
@@ -204,7 +204,7 @@ def train_siamese():
     x2_ = model.inference(x2, reuse=True)
 
     with tf.name_scope('loss'):
-        loss = model.loss(x1_, x2_, y_, 0.2)
+        loss = model.loss(x1_, x2_, y_, margin=1.0)
 
     with tf.name_scope('train'):
[…]

### 2016-12-11 practical_3/train_model.py
trying to get fc2 features

@@ -277,12 +277,14 @@ def feature_extraction():
         session = tf.Session()
         session.run(init)
 
-        new_saver = tf.train.import_meta_graph(CHECKPOINT_DIR_DEFAULT + "/model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt.meta")
-        new_saver.restore(session, CHECKPOINT_DIR_DEFAULT + "/model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt")
+        features = tf.get_collection(tf.GraphKeys.VARIABLES, "ConvNet/fc2/h_f_fc2")
+
+        new_saver = tf.train.import_meta_graph(CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt.meta")
+        new_saver.restore(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt")
 
         batch_x, batch_y = cifar10.train.next_batch(BATCH_SIZE_DEFAULT)
-        x_ = session.run(x_, feed_dict={x: batch_x, y_: batch_y})
-        print(x_)
+        features = session.run(features, feed_dict={x: batch_x, y_: batch_y})
+        print(features)
 
     ########################
     # END OF YOUR CODE    #

### 2016-12-11 practical_3/train_model.py
still not working

@@ -273,17 +273,17 @@ def feature_extraction():
 
         x_ = model.inference(x)
 
+        features = tf.get_collection(tf.get_default_graph().get_tensor_by_name("ConvNet/fc2/h_f_fc2:0"))
+
         init = tf.initialize_all_variables()
         session = tf.Session()
         session.run(init)
-
-        features = tf.get_collection(tf.GraphKeys.VARIABLES, "ConvNet/fc2/h_f_fc2")
 
         new_saver = tf.train.import_meta_graph(CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt.meta")
         new_saver.restore(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt")
 
         batch_x, batch_y = cifar10.train.next_batch(BATCH_SIZE_DEFAULT)
-        features = session.run(features, feed_dict={x: batch_x, y_: batch_y})
+        x_, features = session.run([x_, features], feed_dict={x: batch_x, y_: batch_y})
         print(features)
 
     ########################

### 2016-12-11 practical_3/train_model.py
visualization done

@@ -7,6 +7,9 @@ import os
 
 import tensorflow as tf
 import numpy as np
+from sklearn.manifold import TSNE
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
 from convnet import ConvNet
 from siamese import Siamese
 
@@ -273,7 +276,7 @@ def feature_extraction():
 
         x_ = model.inference(x)
 
-        features = tf.get_collection(tf.get_default_graph().get_tensor_by_name("ConvNet/fc2/h_f_fc2:0"))
+        features = tf.get_default_graph().get_tensor_by_name("ConvNet/flatten/h_f_flatten:0")
 
         init = tf.initialize_all_variables()
         session = tf.Session()
@@ -282,9 +285,24 @@ def feature_extraction():
         new_saver = tf.train.import_meta_graph(CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt.meta")
         new_saver.restore(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt")
 
-        batch_x, batch_y = cifar10.train.next_batch(BATCH_SIZE_DEFAULT)
+        batch_x, batch_y = cifar10.test.images[:1000], cifar10.test.labels[:1000]
         x_, features = session.run([x_, features], feed_dict={x: batch_x, y_: batch_y})
-        print(features)
+
+        tsne = TSNE(n_components=2, verbose=1, perplexity=40, n_iter=300)
+        tsne_result = tsne.fit_transform(features)
+
+
+        plt.figure()
+        colors = cm.rainbow(np.linspace(0, 1, len(batch_y[0])))
+        sizes = np.random.random_integers(25, 50, size=len(batch_y[0]))
+        for i in range(len(batch_y[0])):
+            index = np.where(np.argmax(batch_y, axis=1) == i)
+            plt.scatter(tsne_result[index,0], tsne_result[index,1], c=colors[i], s=sizes[i], label=i)
+        plt.legend(numpoints=1, fontsize=8)
+        plt.show()
+
+
+
 
     ########################
     # END OF YOUR CODE    #

### 2016-12-11 practical_3/train_model.py
restore fixed

@@ -276,21 +276,23 @@ def feature_extraction():
 
         x_ = model.inference(x)
 
-        features = tf.get_default_graph().get_tensor_by_name("ConvNet/flatten/h_f_flatten:0")
+        features_flatten = tf.get_default_graph().get_tensor_by_name("ConvNet/flatten/h_f_flatten:0")
+        features_fc1 = tf.get_default_graph().get_tensor_by_name("ConvNet/fc1/h_f_fc1:0")
+        features_fc2 = tf.get_default_graph().get_tensor_by_name("ConvNet/fc2/h_f_fc2:0")
 
         init = tf.initialize_all_variables()
         session = tf.Session()
         session.run(init)
 
-        new_saver = tf.train.import_meta_graph(CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt.meta")
-        new_saver.restore(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt")
+        saver = tf.train.Saver(tf.all_variables())
+        saver.restore(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt")
 
         batch_x, batch_y = cifar10.test.images[:1000], cifar10.test.labels[:1000]
-        x_, features = session.run([x_, features], feed_dict={x: batch_x, y_: batch_y})
+        x_, features_flatten, features_fc1, features_fc2 = session.run([x_, features_flatten, features_fc1, features_fc2],
+                                                                       feed_dict={x: batch_x, y_: batch_y})
 
         tsne = TSNE(n_components=2, verbose=1, perplexity=40, n_iter=300)
-        tsne_result = tsne.fit_transform(features)
-
+        tsne_result = tsne.fit_transform(features_flatten)
 
         plt.figure()
         colors = cm.rainbow(np.linspace(0, 1, len(batch_y[0])))
@@ -299,9 +301,25 @@ def feature_extraction():
             index = np.where(np.argmax(batch_y, axis=1) == i)
             plt.scatter(tsne_result[index,0], tsne_result[index,1], c=colors[i], s=sizes[i], label=i)
         plt.legend(numpoints=1, fontsize=8)
-        plt.show()
+        plt.savefig("visualization-linear-features_flatten.pdf", bbox_inches = 'tight')
 
[…]

### 2016-12-11 practical_3/report/report_methenitis.tex
visualization done
Visualization for siamese

@@
 \author{
-  David S.~Hippocampus \\
-  \texttt{hippo@cs.cranberry-lemon.edu}
+  Georgios Methenitis \\
+  \texttt{georgios.methenitis@cwi.nl}
 }
@@
 
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.4\textwidth]{visualization-linear-features_flatten.pdf}\\	
+\includegraphics[width=0.49\textwidth]{visualization-linear-features_fc1.pdf}\	
+\includegraphics[width=0.49\textwidth]{visualization-linear-features_fc2.pdf}
+\caption{Visualization of the features in the 2-d space of the \texttt{flatten} layer (top), \texttt{fc1} (bottom-left), \texttt{fc2} (bottom-right).}
+\label{fig:5}
+\end{figure}
+
 \section{Task 3}

### 2016-12-11 practical_3/cifar10_siamese_utils.py

@@ -188,8 +188,6 @@ def create_dataset(source_data, num_tuples = 500, batch_size = 128, fraction_sam
         x1 = np.array([source_data.train._images[index_x1] for i in range(batch_size)])
         x2 = source_data.train._images[index_x2_similar]
         x2 = np.vstack((x2, source_data.train._images[index_x2_opposite]))
-        assert [source_data.train._labels[index_x1] == source_data.train._labels[x] for x in index_x2_similar]
-        assert [source_data.train._labels[index_x1] != source_data.train._labels[x] for x in index_x2_opposite]
         labels = np.hstack((np.ones((n_correct)), np.zeros((batch_size - n_correct))))
         dset.append((x1, x2, labels))
     ########################
@@ -297,9 +295,7 @@ class DataSet(object):
 
       x1 = np.array([self._images[index_x1] for i in range(batch_size)])
       x2 = self._images[index_x2_similar]
-      assert [self._labels[index_x1] == self._labels[x] for x in index_x2_similar]
       x2 = np.vstack((x2, self._images[index_x2_opposite]))
-      assert [self._labels[index_x1] != self._labels[x] for x in index_x2_opposite]
       labels = np.hstack((np.ones((n_correct)), np.zeros((batch_size - n_correct))))
 
     ########################

### 2016-12-11 practical_3/siamese.py

@@ -91,7 +91,7 @@ class Siamese(object):
 
                 h_fc2 = tf.nn.relu(tf.matmul(h_fc1, w_fc2) + b_fc2, name="h_f_fc2")
 
-            l2_out = h_fc2
+            l2_out = tf.nn.l2_normalize(h_fc2, dim=1, name="l_2-norm")
             ########################
             # END OF YOUR CODE    #
             ########################

### 2016-12-11 practical_3/train_model.py

@@ -8,6 +8,8 @@ import os
 import tensorflow as tf
 import numpy as np
 from sklearn.manifold import TSNE
+from sklearn.multiclass import OneVsRestClassifier
+from sklearn.svm import SVC
 import matplotlib.pyplot as plt
 import matplotlib.cm as cm
 from convnet import ConvNet
@@ -230,8 +232,6 @@ def train_siamese():
 
         train_writer.add_summary(summary, iteration)
 
-        print(iteration, l)
-
         if iteration % CHECKPOINT_FREQ_DEFAULT == 0:
             saver.save(session, CHECKPOINT_DIR_DEFAULT + "/siamese-model-at-" + str(iteration) + ".ckpt")
 
@@ -269,57 +269,118 @@ def feature_extraction():
     # PUT YOUR CODE HERE  #
     ########################
     if FLAGS.train_model == 'linear':
-        model = ConvNet()
 
-        x = tf.placeholder(tf.float32, shape=[None, 32, 32, 3])
-        y_ = tf.placeholder(tf.float32, shape=[None, 10])
+        with tf.device('/cpu:0'):
+            model = ConvNet()
 
-        x_ = model.inference(x)
+            x = tf.placeholder(tf.float32, shape=[None, 32, 32, 3])
+            y_ = tf.placeholder(tf.float32, shape=[None, 10])
 
-        features_flatten = tf.get_default_graph().get_tensor_by_name("ConvNet/flatten/h_f_flatten:0")
-        features_fc1 = tf.get_default_graph().get_tensor_by_name("ConvNet/fc1/h_f_fc1:0")
-        features_fc2 = tf.get_default_graph().get_tensor_by_name("ConvNet/fc2/h_f_fc2:0")
+            x_ = model.inference(x)
 
-        init = tf.initialize_all_variables()
-        session = tf.Session()
-        session.run(init)
+            features_flatten = tf.get_default_graph().get_tensor_by_name("ConvNet/flatten/h_f_flatten:0")
+            features_fc1 = tf.get_default_graph().get_tensor_by_name("ConvNet/fc1/h_f_fc1:0")
+            features_fc2 = tf.get_default_graph().get_tensor_by_name("ConvNet/fc2/h_f_fc2:0")
 
-        saver = tf.train.Saver(tf.all_variables())
-        saver.restore(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt")
[…]

### 2016-12-11 practical_3/convnet.py
fixed bias variables in siamese

@@ -57,7 +57,8 @@ class ConvNet(object):
                                           shape=[5, 5, 3, 64],
                                           initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                b_conv1 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
+                b_conv1 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
+
 
                 h_conv1 = tf.nn.relu(tf.nn.conv2d(x, w_conv1, strides=[1, 1, 1, 1], padding='SAME') + b_conv1)
 
@@ -68,7 +69,7 @@ class ConvNet(object):
                                           shape=[5, 5, 64, 64],
                                           initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                b_conv2 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
+                b_conv2 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
 
                 h_conv2 = tf.nn.relu(tf.nn.conv2d(h_pool1, w_conv2, strides=[1, 1, 1, 1], padding='SAME') + b_conv2)
 
@@ -85,7 +86,7 @@ class ConvNet(object):
                                         shape=[flatten.get_shape()[1], 384],
                                         initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                b_fc1 = tf.Variable(tf.constant(0.0, shape=[384]), name='biases')
+                b_fc1 = tf.get_variable('biases', shape=[384], initializer=tf.constant_initializer(0.0))
 
                 h_fc1 = tf.nn.relu(tf.matmul(flatten, w_fc1) + b_fc1, name="h_f_fc1")
 
@@ -94,7 +95,7 @@ class ConvNet(object):
                                         shape=[384, 192],
                                         initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                b_fc2 = tf.Variable(tf.constant(0.0, shape=[192]), name='biases')
+                b_fc2 = tf.get_variable('biases', shape=[192], initializer=tf.constant_initializer(0.0))
 
                 h_fc2 = tf.nn.relu(tf.matmul(h_fc1, w_fc2) + b_fc2, name="h_f_fc2")
 
@@ -103,7 +104,7 @@ class ConvNet(object):
                                         shape=[192, 10],
[…]

### 2016-12-11 practical_3/siamese.py

@@ -50,7 +50,7 @@ class Siamese(object):
                                           shape=[5, 5, 3, 64],
                                           initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                b_conv1 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
+                b_conv1 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
 
                 h_conv1 = tf.nn.relu(tf.nn.conv2d(x, w_conv1, strides=[1, 1, 1, 1], padding='SAME') + b_conv1)
 
@@ -61,7 +61,7 @@ class Siamese(object):
                                           shape=[5, 5, 64, 64],
                                           initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                b_conv2 = tf.Variable(tf.constant(0.0, shape=[64]), name='biases')
+                b_conv2 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
 
                 h_conv2 = tf.nn.relu(tf.nn.conv2d(h_pool1, w_conv2, strides=[1, 1, 1, 1], padding='SAME') + b_conv2)
 
@@ -78,7 +78,7 @@ class Siamese(object):
                                         shape=[flatten.get_shape()[1], 384],
                                         initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                b_fc1 = tf.Variable(tf.constant(0.0, shape=[384]), name='biases')
+                b_fc1 = tf.get_variable('biases', shape=[384], initializer=tf.constant_initializer(0.0))
 
                 h_fc1 = tf.nn.relu(tf.matmul(flatten, w_fc1) + b_fc1, name="h_f_fc1")
 
@@ -87,7 +87,7 @@ class Siamese(object):
                                         shape=[384, 192],
                                         initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                b_fc2 = tf.Variable(tf.constant(0.0, shape=[192]), name='biases')
+                b_fc2 = tf.get_variable('biases', shape=[192], initializer=tf.constant_initializer(0.0))
 
                 h_fc2 = tf.nn.relu(tf.matmul(h_fc1, w_fc2) + b_fc2, name="h_f_fc2")
 

### 2016-12-11 practical_3/train_model.py

@@ -232,6 +232,8 @@ def train_siamese():
 
         train_writer.add_summary(summary, iteration)
 
+        print(iteration, l)
+
         if iteration % CHECKPOINT_FREQ_DEFAULT == 0:
             saver.save(session, CHECKPOINT_DIR_DEFAULT + "/siamese-model-at-" + str(iteration) + ".ckpt")
 
@@ -288,7 +290,6 @@ def feature_extraction():
 
             saver = tf.train.Saver(tf.all_variables())
             saver.restore(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt")
-
 
             batch_x, batch_y = cifar10.test.images, cifar10.test.labels
             x_, features_flatten, features_fc1, features_fc2 = session.run([x_, features_flatten, features_fc1, features_fc2], feed_dict={x: batch_x, y_: batch_y})
@@ -445,7 +446,7 @@ if __name__ == '__main__':
                       help='Summaries log directory')
     parser.add_argument('--checkpoint_dir', type = str, default = CHECKPOINT_DIR_DEFAULT,
                       help='Checkpoint directory')
-    parser.add_argument('--is_train', type = str, default = False,
+    parser.add_argument('--is_train', type = str, default = True,
                       help='Training or feature extraction')
     parser.add_argument('--train_model', type = str, default = 'siamese',
                       help='Type of model. Possible options: linear and siamese')

### 2016-12-12 practical_3/convnet.py
1-vs-all and several fixes

@@ -3,6 +3,8 @@ from __future__ import division
 from __future__ import print_function
 
 import tensorflow as tf
+from tensorflow.contrib.layers import initializers
+from tensorflow.contrib.layers import regularizers
 
 class ConvNet(object):
     """
@@ -55,10 +57,10 @@ class ConvNet(object):
             with tf.variable_scope('conv1') as scope:
                 w_conv1 = tf.get_variable('weights',
                                           shape=[5, 5, 3, 64],
-                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001),
+                                          regularizer=regularizers.l2_regularizer(0.001))
 
                 b_conv1 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
-
 
                 h_conv1 = tf.nn.relu(tf.nn.conv2d(x, w_conv1, strides=[1, 1, 1, 1], padding='SAME') + b_conv1)
 
@@ -67,7 +69,8 @@ class ConvNet(object):
             with tf.variable_scope('conv2') as scope:
                 w_conv2 = tf.get_variable('weights',
                                           shape=[5, 5, 64, 64],
-                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001),
+                                          regularizer=regularizers.l2_regularizer(0.001))
 
                 b_conv2 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
 
@@ -84,7 +87,8 @@ class ConvNet(object):
             with tf.variable_scope('fc1') as scope:
                 w_fc1 = tf.get_variable('weights',
                                         shape=[flatten.get_shape()[1], 384],
-                                        initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+                                        initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001),
+                                        regularizer=regularizers.l2_regularizer(0.001))
 
                 b_fc1 = tf.get_variable('biases', shape=[384], initializer=tf.constant_initializer(0.0))
 
@@ -93,7 +97,8 @@ class ConvNet(object):
             with tf.variable_scope('fc2') as scope:
                 w_fc2 = tf.get_variable('weights',
[…]

### 2016-12-12 practical_3/siamese.py

@@ -5,7 +5,8 @@ from __future__ import print_function
 import tensorflow as tf
 import numpy as np
 
-
+from tensorflow.contrib.layers import initializers
+from tensorflow.contrib.layers import regularizers
 
 class Siamese(object):
     """
@@ -48,7 +49,8 @@ class Siamese(object):
             with tf.variable_scope('conv1', reuse=reuse) as scope:
                 w_conv1 = tf.get_variable('weights',
                                           shape=[5, 5, 3, 64],
-                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+                                          initializer=initializers.xavier_initializer(),
+                                          regularizer=regularizers.l2_regularizer(0.001))
 
                 b_conv1 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
 
@@ -59,7 +61,8 @@ class Siamese(object):
             with tf.variable_scope('conv2', reuse=reuse) as scope:
                 w_conv2 = tf.get_variable('weights',
                                           shape=[5, 5, 64, 64],
-                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+                                          initializer=initializers.xavier_initializer(),
+                                          regularizer=regularizers.l2_regularizer(0.001))
 
                 b_conv2 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
 
@@ -76,7 +79,8 @@ class Siamese(object):
             with tf.variable_scope('fc1', reuse=reuse) as scope:
                 w_fc1 = tf.get_variable('weights',
                                         shape=[flatten.get_shape()[1], 384],
-                                        initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+                                        initializer=initializers.xavier_initializer(),
+                                        regularizer=regularizers.l2_regularizer(0.001))
 
                 b_fc1 = tf.get_variable('biases', shape=[384], initializer=tf.constant_initializer(0.0))
 
@@ -85,13 +89,14 @@ class Siamese(object):
             with tf.variable_scope('fc2', reuse=reuse) as scope:
                 w_fc2 = tf.get_variable('weights',
                                         shape=[384, 192],
-                                        initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
[…]

### 2016-12-12 practical_3/train_model.py

@@ -21,7 +21,7 @@ import cifar10_siamese_utils
 LEARNING_RATE_DEFAULT = 1e-4
 BATCH_SIZE_DEFAULT = 128
 MAX_STEPS_DEFAULT = 15000
-EVAL_FREQ_DEFAULT = 1000
+EVAL_FREQ_DEFAULT = 15000
 CHECKPOINT_FREQ_DEFAULT = 5000
 PRINT_FREQ_DEFAULT = 10
 OPTIMIZER_DEFAULT = 'ADAM'
@@ -209,7 +209,7 @@ def train_siamese():
     x2_ = model.inference(x2, reuse=True)
 
     with tf.name_scope('loss'):
-        loss = model.loss(x1_, x2_, y_, margin=1.0)
+        loss = model.loss(x1_, x2_, y_, margin=0.2)
 
     with tf.name_scope('train'):
         train_step = tf.train.AdamOptimizer(LEARNING_RATE_DEFAULT).minimize(loss)
@@ -291,7 +291,7 @@ def feature_extraction():
             saver = tf.train.Saver(tf.all_variables())
             saver.restore(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt")
 
-            batch_x, batch_y = cifar10.test.images, cifar10.test.labels
+            batch_x, batch_y = cifar10.test.images[:1000], cifar10.test.labels[:1000]
             x_, features_flatten, features_fc1, features_fc2 = session.run([x_, features_flatten, features_fc1, features_fc2], feed_dict={x: batch_x, y_: batch_y})
 
         '''
@@ -305,56 +305,65 @@ def feature_extraction():
             sizes = np.random.random_integers(25, 50, size=len(batch_y[0]))
             for i in range(len(batch_y[0])):
                 index = np.where(np.argmax(batch_y, axis=1) == i)
-                plt.scatter(tsne_result[index,0], tsne_result[index,1], c=colors[i], s=sizes[i], label=i)
+                plt.scatter(tsne_result[index,0], tsne_result[index, 1], c=colors[i], s=sizes[i], label=i)
             plt.legend(numpoints=1, fontsize=8)
-            plt.savefig("visualization-linear-features_flatten.pdf", bbox_inches = 'tight')
+            # plt.savefig("visualization-linear-features_flatten.pdf", bbox_inches = 'tight')
+            # plt.show()
 
[…]

### 2016-12-12 practical_3/siamese.py
update

@@ -49,7 +49,7 @@ class Siamese(object):
             with tf.variable_scope('conv1', reuse=reuse) as scope:
                 w_conv1 = tf.get_variable('weights',
                                           shape=[5, 5, 3, 64],
-                                          initializer=initializers.xavier_initializer(),
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001),
                                           regularizer=regularizers.l2_regularizer(0.001))
 
                 b_conv1 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
@@ -61,7 +61,7 @@ class Siamese(object):
             with tf.variable_scope('conv2', reuse=reuse) as scope:
                 w_conv2 = tf.get_variable('weights',
                                           shape=[5, 5, 64, 64],
-                                          initializer=initializers.xavier_initializer(),
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001),
                                           regularizer=regularizers.l2_regularizer(0.001))
 
                 b_conv2 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
@@ -79,7 +79,7 @@ class Siamese(object):
             with tf.variable_scope('fc1', reuse=reuse) as scope:
                 w_fc1 = tf.get_variable('weights',
                                         shape=[flatten.get_shape()[1], 384],
-                                        initializer=initializers.xavier_initializer(),
+                                        initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001),
                                         regularizer=regularizers.l2_regularizer(0.001))
 
                 b_fc1 = tf.get_variable('biases', shape=[384], initializer=tf.constant_initializer(0.0))
@@ -89,14 +89,14 @@ class Siamese(object):
             with tf.variable_scope('fc2', reuse=reuse) as scope:
                 w_fc2 = tf.get_variable('weights',
                                         shape=[384, 192],
-                                        initializer=initializers.xavier_initializer(),
+                                        initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001),
                                         regularizer=regularizers.l2_regularizer(0.001))
 
[…]

### 2016-12-12 practical_3/train_model.py

@@ -21,7 +21,7 @@ import cifar10_siamese_utils
 LEARNING_RATE_DEFAULT = 1e-4
 BATCH_SIZE_DEFAULT = 128
 MAX_STEPS_DEFAULT = 15000
-EVAL_FREQ_DEFAULT = 15000
+EVAL_FREQ_DEFAULT = 1000
 CHECKPOINT_FREQ_DEFAULT = 5000
 PRINT_FREQ_DEFAULT = 10
 OPTIMIZER_DEFAULT = 'ADAM'
@@ -397,7 +397,7 @@ def feature_extraction():
             test_set = range(train_set[0], features.shape[0])
             classif = OneVsRestClassifier(SVC(kernel='linear'))
             classif.fit(features[train_set], batch_y[train_set])
-            print("Accuracy with flatten:",
+            print("Accuracy with l_2-norm:",
                   classif.score(features[test_set], batch_y[test_set]))
 
 
@@ -463,7 +463,7 @@ if __name__ == '__main__':
                       help='Summaries log directory')
     parser.add_argument('--checkpoint_dir', type = str, default = CHECKPOINT_DIR_DEFAULT,
                       help='Checkpoint directory')
-    parser.add_argument('--is_train', type = str, default = False,
+    parser.add_argument('--is_train', type = str, default = True,
                       help='Training or feature extraction')
     parser.add_argument('--train_model', type = str, default = 'siamese',
                       help='Type of model. Possible options: linear and siamese')

### 2016-12-12 practical_3/train_model.py
update

@@ -379,7 +379,7 @@ def feature_extraction():
         '''
             VISUALIZATION
         '''
-        if 0:
+        if 1:
             tsne = TSNE(n_components=2, verbose=1, perplexity=40, n_iter=300)
             tsne_result = tsne.fit_transform(features)
             plt.figure()

### 2016-12-16 practical_3/report/report_methenitis.tex
1-vs-all and several fixes
update

@@
 
-\title{Report for the Deep Learning Course Assignment 2 }
+\title{Report for the Deep Learning Course Assignment 3}
 
@@
 \begin{document}
-% \nipsfinalcopy is no longer used
 
@@
 \begin{abstract}
-Should contain information about the current task and the summary of the study of the CNN models on CIFAR10 dataset.
+In this assignment I implemented a convolutional neural network (CNN) with two different architectures on the CIFAR10 dataset.
+The first was a straightforward architecture where the input image was fed into a single neural network, while the goal of the neural network was to identify the class of the image.
+In the second architecture, two images were the input of two copies of the same neural network, while the goal of the learning was to distinguish between two different images' classes.
+In all experiments I used a desktop computer equipped with an NVIDIA GTX770 GPU with 2GB of ram.
 
@@
 \section{Task 1}
-Should contain all needed information about Task 1 and report of all your experiments for that task.
+In this section I explain the implementation and present the results of the first task of the assignment.
+I implemented the architecture for the CNN as this was given in the assignment.
+For the initialization and regularization of the weights I used:
+\begin{verbatim}
+initializer = tf.random_normal_initializer( mean=0.0, stddev=0.001 )
+regularizer = regularizers.l2_regularizer( 0.001 )
+\end{verbatim}
+but also experimented with xavier initializer without however reporting the results here, since there was no improvement over the normal distributed initialization of the weights.
+Furthermore all biases were initialized at zero:
+\begin{verbatim}
+initializer=tf.constant_initializer(0.0))
+\end{verbatim}
+Figure~\ref{fig:1} illustrates the accuracy and the loss during training and test without regularization.
+\begin{figure}[h!]
+\centering
+\includegraphics[height=4.0cm]{acc-plain.png}\
+\includegraphics[height=4.0cm]{loss-plain.png}
+\caption{Accuracy (left) and loss (right) for the CNN with batch size of $128$ and no regularization. Green lines illustrate performance on the training set and blue lines on the test set.}
+\label{fig:1}
+\end{figure}
+As shown in the Figures~\ref{fig:1}, the model overfits the training data.
+The accuracy in the training set approximates $1.0$ in the last $5000$ steps of the training where the loss in the test set is increasing while accuracy in the test set is not affected.
 
-Figure~\ref{fig:1}, \ref{fig:2}
+\subsection{Regularization}
+\label{sec:reg}
+
+In this section I present the results of the CNN with regularization losses in the weights.
+More specifically I added regularization losses in the fully connected layers $fc1, fc2$
+\begin{verbatim}
+if self.wd is not None:
+    weight_decay = tf.mul(tf.nn.l2_loss(w_fc1), self.wd, name='weight_loss')
+    tf.add_to_collection('losses', weight_decay)
+\end{verbatim}
+making sure the losses were added to the loss function in the loss function of convNet class.
+Figure~\ref{fig:2} illustrates the accuracy and the loss during training and test with regularization $wd=0.005$.
+\begin{figure}[h!]
+\centering
+\includegraphics[height=4.0cm]{acc-plain-reg.png}\
+\includegraphics[height=4.0cm]{loss-plain-reg.png}
+\caption{Accuracy (left) and loss (right) for the CNN with batch size of $128$ and no regularization. Cyan lines illustrate performance on the training set and orange lines on the test set.}
+\label{fig:2}
+\end{figure}
+There is no performance gain by the regularization apart from a decrease in the loss in the test set.
+
+\subsection{Dropout}
+
+In the next experiment I implemented dropout in the fully connected layers $fc1, fc2$.
+\begin{verbatim}
+h_fc1 = tf.cond(tf.cast(self.isTrain, tf.bool), 
+lambda: tf.nn.dropout(h_fc1, 0.8), lambda: h_fc1)
+\end{verbatim}
+Figure~\ref{fig:3} illustrates the accuracy and the loss during training and test with dropout $0.5, 0.2$.
+\begin{figure}[h!]
+\centering
+\includegraphics[height=4.0cm]{acc-plain-drop.png}\
+\includegraphics[height=4.0cm]{loss-plain-drop.png}
+\caption{Accuracy (left) and loss (right) for the CNN with batch size of $128$ and dropout.
+Red lines illustrate performance on the training set and purple lines on the test set for dropout $0.2$, while light green lines illustrate performance on the training set and yellow lines on the test set for dropout $0.5$.}
+\label{fig:3}
+\end{figure}
+The performance on the test set in the end of the training was:
+\begin{itemize}
+\item For no dropout: $\mathbf{0.7503}$
+\item For dropout $0.5$: $0.7324$
+\item For dropout $0.2$: $0.7433$
+\end{itemize}
+There was no performance gain, but only a decrease in overfitting with dropout $0.5$.
+
+\subsection{Smaller Batch Size}
+
+Here, I used half the size of the batch to complete training using batch size of $64$.
+Figure~\ref{fig:4} illustrates the accuracy and the loss during training and test with the given batch size of $128$ and the half batch size of $64$.
 
@@
 \centering
-\includegraphics[height=3.2cm]{acc1.png}\	
-\includegraphics[height=3.2cm]{loss1.png}
-\caption{Accuracy (left) and loss on the training set with batch size of $128$ samples. The accuracy approximates $1.0$ in the training set implying that the model overfits the training set.}
-\label{fig:1}
+\includegraphics[height=4.0cm]{acc-linear-64.png}\
+\includegraphics[height=4.0cm]{loss-linear-64.png}
+\caption{Accuracy (left) and loss (right) for the CNN with batch size of $64$.
+Cyan lines illustrate performance on the training set and orange lines on the test set for dropout $0.2$.
+Green and blue lines illustrate the performance of batch size $128$ with default configuration CNN as in all previous figures.}
+\label{fig:4}
+\end{figure}
+The performance on the test set in the end of the training was:
+\begin{itemize}
+\item For batch size $128$: $0.7503$
+\item For batch size $64$: $\mathbf{0.7520}$
+\end{itemize}
+There was a performance gain by using smaller batch size and a limited overfitting.
+
+\subsubsection{Regularization}
+As in Section~\ref{sec:reg} I used regularization for the weights in the fully connected layers $fc1, fc2$.
+Figure~\ref{fig:5} illustrates the accuracy and the loss during training and test with the given batch size of $64$ two regularization values for the weight decays.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[height=4.0cm]{acc-linear-64-reg.png}\
+\includegraphics[height=4.0cm]{loss-linear-64-reg.png}
+\caption{Accuracy (left) and loss (right) for the CNN with batch size of $64$.
+Cyan lines illustrate performance on the training set and orange lines on the test set without weight regularization.
+Red lines illustrate performance on the training set and purple lines on the test set with weight regularization $0.01$.
+Light purple lines illustrate performance on the training set and cyan lines on the test set with weight regularization $0.005$.}
+\label{fig:5}
+\end{figure}
+The performance on the test set in the end of the training was:
+\begin{itemize}
+\item No regularization: $0.7520$
+\item For regularization $0.01$: $\mathbf{0.7634}$
+\item For regularization $0.005$: $0.7569$
+\end{itemize}
+The maximum reported accuracy on the test set was achieved by using mini batches of $64$ size and regularization values of $0.01$.
+
+\subsubsection{Dropout}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[height=4.0cm]{acc-linear-64-drop.png}\
+\includegraphics[height=4.0cm]{loss-linear-64-drop.png}
+\caption{Accuracy (left) and loss (right) for the CNN with batch size of $64$.
+Cyan lines illustrate performance on the training set and orange lines on the test set without weight regularization.
+Red lines illustrate performance on the training set and purple lines on the test set with weight regularization $0.01$.
+Light purple lines illustrate performance on the training set and cyan lines on the test set with weight regularization $0.005$.}
+\label{fig:6}
+\end{figure}
+
+The performance on the test set in the end of the training was:
+\begin{itemize}
+\item No dropout: $0.7520$
+\item For dropout $0.5$: $0.7279$
+\item For dropout $0.2$: $0.7493$
+\end{itemize}
+The was no performance gain by using dropout when using smaller batches of $64$ size.
+
+\subsection{Feature Visualization}
+
+In this section I show how the features learned during training of the CNN can be illustrated and how they can be used to train an one-vs-all classifier.
+I load the learned weights during training and converting them to $2$-d points using TSNE.
+\begin{verbatim}
+tsne = TSNE(n_components=2, verbose=1, perplexity=40, n_iter=300)
+tsne.fit_transform(features)
+\end{verbatim}
+Figure~\ref{fig:7} presents the visualization of the features in the two dimensional space. 
+You can observe that features obtained in $fc2$ layer can distinguish better features of different classes.
+On the contrary when see the flatten features all labels are located close to points of other classes.
+\begin{figure}[h!]
+\centering
+\includegraphics[height=5.0cm]{visualization-linear-features_flatten.pdf}
+\includegraphics[height=5.0cm]{visualization-linear-features_fc1.pdf}
+\includegraphics[height=5.0cm]{visualization-linear-features_fc2.pdf}
+\caption{Visualization of the features in the 2-d space of the \texttt{flatten} layer (top), \texttt{fc1} (bottom-left), \texttt{fc2} (bottom-right).}
+\label{fig:7}
+\end{figure}
+
+\subsubsection{One-vs-Rest Classifier}
+
+To test the accuracy of the one-vs-all classifier I use the features retained by the learned model to train the classifiers.
+Using the 80 percent of the features I train a linear kernel OneVsRest classifier, and test the accuracy over the rest 20 percent.
+\begin{verbatim}
+train_set = range(int(features.shape[0]*0.8))
+test_set = range(train_set[-1] + 1, features.shape[0])
+
+classif = OneVsRestClassifier(SVC(kernel='linear'))
+classif.fit(features[train_set], batch_y[train_set]
+classif.score(features[test_set], batch_y[test_set]
+\end{verbatim}
+Here, the reported accuracy of the one-vs-classifiers on the test set:
+\begin{itemize}
+\item Accuracy with flatten features: $0.6306$.
+\item Accuracy with fc1 features: $0.$.
+\item Accuracy with fc2 features: $0.$.
+\end{itemize}
+It is natural that the accuracy is higher for later layers.
+As it was earlier $fc2$ layer can distinguish better features of different classes.
+
+\section{Task 2}
+
+In this section I present my implementation and the results achieved by the siamese architecture of the CNN.
+First, I implemented the functions \texttt{create\_dataset} and \texttt{next\_batch} in the \texttt{cifar10\_siamese\_utils.py}.
+
+\subsection{Dataset}
+
+The create\_dataset function:
+\begin{tiny}
+\begin{verbatim}
+dset = []
+    for sample_tuple in range(num_tuples):
+
+        n_correct = int(fraction_same * batch_size)
+
+        val_set_indexes = range(int(source_data.train._images.shape[0] * 0.8), source_data.train._images.shape[0])
+
+        index_x1 = np.random.choice(val_set_indexes)
+        label_x1 = source_data.train._labels[index_x1]
+
+        index_x2_similar = np.random.choice(val_set_indexes[0] +
+                                            np.where(source_data.train._labels[val_set_indexes] == label_x1)[0],
+                                            replace=False, size=n_correct)
+
+        index_x2_opposite = np.random.choice(val_set_indexes[0] +
+                                             np.where(source_data.train._labels[val_set_indexes] != label_x1)[0],
+                                             replace=False, size=(batch_size - n_correct))
+
+        x1 = np.array([source_data.train._images[index_x1] for i in range(batch_size)])
+        x2 = source_data.train._images[index_x2_similar]
+        x2 = np.vstack((x2, source_data.train._images[index_x2_opposite]))
+        labels = np.hstack((np.ones((n_correct)), np.zeros((batch_size - n_correct))))
+
+        dset.append((x1, x2, labels))
+
+    return dset
+\end{verbatim}
+\end{tiny}
+which returns \texttt{num\_tuples} tuples of the following batches:
+\begin{verbatim}
+      X_1            X_2               Y
+| image_cl1_1, image_cl1_10  | -->   | 1 |
+| image_cl1_1, image_cl1_4   | -->   | 1 |
+| image_cl1_1, image_cl1_163 | -->   | 1 |
+| image_cl1_1, image_cl1_145 | -->   | 1 |
+| image_cl1_1, image_cl3_8   | -->   | 0 |
+|      .            .        | -->   | 0 |
+|      .            .        | -->   | 0 |
+|      .            .        | -->   | 0 |
+| image_cl1_1, image_cl5_8   | -->   | 0 |
+| image_cl1_1, image_cl2_    | -->   | 0 |
+| image_cl1_1, image_cl10_8  | -->   | 0 |
+\end{verbatim}
+and used for the evaluation of the training set.
+
+The \texttt{next\_batch} function, which include the following piece of code was given to us in \texttt{cifar10\_utils.py} to sample as uniformly the dataset as possible.
+\begin{tiny}
+\begin{verbatim}
+n_correct = int(fraction_same * batch_size)
+        val_set_indexes = range(int(self._images.shape[0] * 0.8))
+
+        start = self._index_in_epoch
+        self._index_in_epoch += batch_size
+        if self._index_in_epoch > self._num_examples * 0.8:
+            self._epochs_completed += 1
+            np.random.shuffle(val_set_indexes)
+            start = 0
+            self._index_in_epoch = batch_size
+            assert batch_size <= self._num_examples
+
+        end = self._index_in_epoch
+
+        val_set_indexes = val_set_indexes[start:end]
+\end{tiny}
+\end{verbatim}
+\end{tiny}
+The \texttt{next\_batch} function then creates each training batch in two following ways.
+\begin{itemize}
+\item In the \emph{default} implementation the structure of each batch is the same as the test set following the same idea.
+All images in $x1$ are the same, while $x2$ contains \texttt{fraction} percentage of similar label images to $x1$ and the rest random images of different classes.
+\item In the \emph{alternative} implementation the following piece of code
+\begin{tiny}
+\begin{verbatim}
+random_index = np.array(np.random.choice(val_set_indexes, replace=False, size=batch_size))
+
+matches = [np.random.choice(np.array(np.where(self._labels[range(int(self._images.shape[0] * 0.8))] == 
+self._labels[x]))[0]) for x in random_index]
+
+mismatches = [np.random.choice(np.array(np.where(self._labels[range(int(self._images.shape[0] * 0.8))] != 
+self._labels[x]))[0]) for x in random_index]
+
+x1 = self._images[random_index]
+x2 = self._images[matches[:n_correct]]
+x2 = np.vstack((x2, self._images[mismatches[n_correct:]]))
+labels = np.hstack((np.ones((n_correct)), np.zeros((batch_size-n_correct))))
+\end{verbatim}
+\end{tiny}
+generates batches of random pairs of images respecting the \texttt{fraction} of same label images.
+The resulted batch 
+\begin{verbatim}
+      X_1            X_2               Y
+| image_cl1_10, image_cl1_50   | -->   | 1 |
+| image_cl4_17, image_cl4_234  | -->   | 1 |
+| image_cl8_654, image_cl8_14  | -->   | 1 |
+| image_cl8_66, image_cl6_234  | -->   | 0 |
+|      .            .          | -->   | 0 |
+|      .            .          | -->   | 0 |
+|      .            .          | -->   | 0 |
+| image_cl2_327, image_cl6_234 | -->   | 0 |
+\end{verbatim}
+\end{itemize}
+
+\subsection{Loss function}
+
+I used the following two loss functions:
+\begin{enumerate}
+\item $\mathcal{L} =  Y * \frac{1}{2} * d^2 + (1-Y) * max(margin - d^2, 0)$
+\item $\mathcal{L} =  Y * d^2 + (1-Y) * max(margin - d^2, 0)$
+\end{enumerate}
+
+\subsection{Training}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=10.2cm]{siamese.png}
+\caption{\textbf{Experiment 1} Loss in the training (purple line) and the test set (yellow line) for $50000$ training steps, $margin = 1.0$, using the default \texttt{next\_batch} method and the loss function (1).}
+\label{fig:siamese}
 \end{figure}
@@
 \centering
-\includegraphics[height=3.2cm]{acc2.png}\	
-\includegraphics[height=3.2cm]{loss2.png}
-\caption{Accuracy (left) and loss on the test set with batch size of $128$ samples. The accuracy is $0.88$ after $15000$ steps.}
-\label{fig:2}
-\end{figure}
-
-\subsection{Smaller batch size}
-
-Figure~\ref{fig:3}, \ref{fig:4}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[height=3.2cm]{acc3.png}\	
-\includegraphics[height=3.2cm]{loss3.png}
-\caption{Accuracy (left) and loss on the training set with batch size of $128$ samples. The accuracy approximates $1.0$ in the training set implying that the model overfits the training set.}
-\label{fig:3}
+\includegraphics[width=10.2cm]{siamese-1.png}
+\caption{\textbf{Experiment 2} Loss in the training (blue line) and the test set (light purple line) for $50000$ training steps, $margin = 1.0$, using the default \texttt{next\_batch} method and the loss function (2).
+Loss in the training (purple line) and the test set (yellow line) for $50000$ training steps, $margin = 1.0$, using the default \texttt{next\_batch} method and the loss function (1).}
+\label{fig:siamese-1}
 \end{figure}
@@
 \centering
-\includegraphics[height=3.2cm]{acc4.png}\	
-\includegraphics[height=3.2cm]{loss4.png}
-\caption{Accuracy (left) and loss on the test set with batch size of $128$ samples. The accuracy is $0.88$ after $15000$ steps.}
-\label{fig:4}
+\includegraphics[width=10.2cm]{siamese-2.png}
+\caption{\textbf{Experiment 3} Loss in the training (blue line) and the test set (light purple line) for $50000$ training steps, $margin = 1.0$, using the default \texttt{next\_batch} method and the loss function (2).
+Loss in the training (yellow line) and the test set (light purple line) for $50000$ training steps, $margin = 1.0$, using the default \texttt{next\_batch} method and the loss function (2).}
+\label{fig:siamese-2}
 \end{figure}
 
-\section{Task 2}
-Should contain all needed information about Task 2 and report of all your experiments for that task.
+\subsection{Feature Visualization}
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{visualization-linear-features_flatten.pdf}\\	
-\includegraphics[width=0.49\textwidth]{visualization-linear-features_fc1.pdf}\	
-\includegraphics[width=0.49\textwidth]{visualization-linear-features_fc2.pdf}
-\caption{Visualization of the features in the 2-d space of the \texttt{flatten} layer (top), \texttt{fc1} (bottom-left), \texttt{fc2} (bottom-right).}
-\label{fig:5}
+\includegraphics[width=6.2cm]{visualization-siamese-plain.pdf}
+\includegraphics[width=6.2cm]{visualization-siamese-1.pdf}
+\includegraphics[width=7.2cm]{visualization-siamese-3.pdf}
+\caption{}
+\label{fig:features}
 \end{figure}
 
-\section{Task 3}
-Should contain all needed information about Task 3 and report of all your experiments for that task.
+\subsection{One-vs-Rest Classifier}
+\begin{itemize}
+\textbf{Experiment 1}: $0.476$
+\textbf{Experiment 2}: $0.473$
+\textbf{Experiment 3}: $0.682$
+\end{itemize}
 
-\section{Conclusion}
-Should contain conclusion of this study.
-
-%\section*{References}
+%Figure~\ref{fig:6} illustrates the loss in the training and the test set using the normal implementation of the batch creation.
+%The siamese network learning converges after $12000$ steps.
+%The network seems to learn the features that minimize the loss.
+%Figure~\ref{fig:7} presents four different implementations using different parameters.
 %
-%\small
 %
-%[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
-%for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
-%T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
-%  Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.
+%\begin{figure}[h!]
+%\centering
+%\includegraphics[width=7.2cm]{loss-siamese-train-1.png}\	
+%\includegraphics[width=6.6cm]{loss-siamese-test-1.pdf}
+%\caption{Loss in the training (Left) and the test set (Right - green line) for $15000$ training steps, $margin = 0.2$, and weight regularization loss.}
+%\label{fig:6}
+%\end{figure}
 %
-%[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
-%  Exploring Realistic Neural Models with the GEneral NEural SImulation
-%  System.}  New York: TELOS/Springer--Verlag.
 %
-%[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
-%learning and recall at excitatory recurrent synapses and cholinergic
-%modulation in rat hippocampal region CA3. {\it Journal of
-%  Neuroscience} {\bf 15}(7):5249-5262.
+%\begin{figure}[h!]
+%\centering
+%\includegraphics[width=0.4\textwidth]{loss-siamese-train-1}
+%\includegraphics[width=0.4\textwidth]{loss-siamese-train-2}
+%\includegraphics[width=0.4\textwidth]{loss-siamese-train-3}
+%\includegraphics[width=0.4\textwidth]{loss-siamese-train-4}
+%\caption{Visualization of the $l2$-normalized features in the output of the CNN for $5000$ samples of the test set.
+For $margin=0.2$ with weight normalization (top-left), for $margin=1.0$ with weight normalization (top-right), and without normalization (bottom-left).
+Last, the visualization of the features when the alternative way of creating batches is used (bottom-right).
+%For $margin=1.0$ the alternative way of creating batches is reducing the loss.}
+%\label{fig:7}
+%\end{figure}
+%
+%
+%\subsection{Feature Visualization}
+%
+%
+%Using the same TSNE algorithm we present the $2$-dimensional representation of the features for the siamese architecture.
+Figure~\ref{fig:8} presents the $2$-d representation of the features over $5000$ samples of the test set, for the four different implementation showed in Figure~\ref{fig:7}.
+%
+%\begin{figure}[h!]
+%\centering
+%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2.pdf}
+%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2-1.pdf}
+%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2-2.pdf}
+%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2-3.pdf}
+%\caption{Visualization of the $l2$-normalized features in the output of the CNN for $5000$ samples of the test set.
+For $margin=0.2$ with weight normalization (top-left), for $margin=1.0$ with weight normalization (top-right), and without normalization (bottom-left).
+Last, the visualization of the features when the alternative way of creating batches is used $margin = 1.0$ and without weight normalization (bottom-right).}
+%\label{fig:8}
+%\end{figure}
+%
+%\subsection{One-vs-All Classifiers}
+%
+%For the four different implementation parameters that were presented in the Figure~\ref{fig:7} and \ref{fig:8} the accuracy of the one-vs-all classifier that is achieved:
+%\begin{itemize}
+%\item Accuracy with l\_2-norm: $0.0957$
+%\item Accuracy with l\_2-norm: $0.121$
+%\item Accuracy with l\_2-norm: $0.1048$
+%\item Accuracy with l\_2-norm: $0.1564$
+%\end{itemize}
+%I showed that the loss was reduced by using the alternative way of sampling batches, here the accuracy of the classifier is increased as well.
+%Figure
+%
+%
+%\subsection{Update for Task 2}
+%
+%In this section I provide the results of a last experiment where I used $50000$ training steps.
+%The model seems to learn and distinguishes between different classes.
+%Figure~\ref{fig:9} presents the loss in the training set.
+%
+%
+%
+%\begin{figure}[h!]
+%\centering
+%\includegraphics[width=0.8\textwidth]{loss-siamese-final.png}
+%\caption{Loss of the siamese architecture of the CNN in the training procedure for $50000$ training steps. For $margin=1.0$ without weight normalization.}
+%\label{fig:9}
+%\end{figure}
+%
+%Figure~\ref{fig:10} presents the visualized in $2-d$ features.
+%
+%\begin{figure}[h!]
+%\centering
+%\includegraphics[width=0.8\textwidth]{visualization-siamese-features_fc2-4.pdf}
+%\caption{Visualization of the $l2$-normalized features in the output of the CNN for all samples of the test set. For $margin=1.0$ without weight normalization.}
+%\label{fig:10}
+%\end{figure}
+%
+%To test the accuracy of the one-vs-all classifier I use the features retained by the learned model to train the classifiers.
+%Using the 80 percent of the features I train a linear kernel OneVsRest classifier, and test the accuracy over the rest 20 percent.
+%The reported accuracy over the test set is:
+%\begin{itemize}
+%\item Accuracy with l\_2-norm: $0.6789$
+%\end{itemize}
+%
+%
+%
+%\section{Conclusion}
+%
+%In this assignment I implemented a CNN and reported its performance over the CIFAR10 dataset using different parameters.
+%I also implemented the siamese architecture which uses two versions of the same CNN to perform learning in order to distinguish between classes.
+%The amount of training steps requires for the siamese are higher than the single CNN architecture.
+%The time required for the experiments did not let me try more parameter values, therefore I cannot draw any important conclusions regarding the right parameters that should be used for the two different approaches.
 

### 2016-12-16 practical_3/cifar10_siamese_utils.py

@@ -18,109 +18,114 @@ from tensorflow.contrib.learn.python.learn.datasets import base
 # Default paths for downloading CIFAR10 data
 CIFAR10_FOLDER = 'cifar10/cifar-10-batches-py'
 
+
 def load_cifar10_batch(batch_filename):
-  """
-  Loads single batch of CIFAR10 data.
-  Args:
-    batch_filename: Filename of batch to get data from.
-  Returns:
-    X: CIFAR10 batch data in numpy array with shape (10000, 32, 32, 3).
-    Y: CIFAR10 batch labels in numpy array with shape (10000, ).
-  """
-  with open(batch_filename, 'rb') as f:
-    batch = pickle.load(f)
-    X = batch['data']
-    Y = batch['labels']
-    X = X.reshape(10000, 3, 32, 32).transpose(0,2,3,1).astype(np.float32)
-    Y = np.array(Y)
-    return X, Y
+    """
+    Loads single batch of CIFAR10 data.
+    Args:
+      batch_filename: Filename of batch to get data from.
+    Returns:
+      X: CIFAR10 batch data in numpy array with shape (10000, 32, 32, 3).
+      Y: CIFAR10 batch labels in numpy array with shape (10000, ).
+    """
+    with open(batch_filename, 'rb') as f:
+        batch = pickle.load(f)
+        X = batch['data']
+        Y = batch['labels']
+        X = X.reshape(10000, 3, 32, 32).transpose(0, 2, 3, 1).astype(np.float32)
+        Y = np.array(Y)
+        return X, Y
+
 
 def load_cifar10(cifar10_folder):
-  """
-  Loads CIFAR10 train and test splits.
-  Args:
-    cifar10_folder: Folder which contains downloaded CIFAR10 data.
-  Returns:
-    X_train: CIFAR10 train data in numpy array with shape (50000, 32, 32, 3).
-    Y_train: CIFAR10 train labels in numpy array with shape (50000, ).
-    X_test: CIFAR10 test data in numpy array with shape (10000, 32, 32, 3).
-    Y_test: CIFAR10 test labels in numpy array with shape (10000, ).
+    """
+    Loads CIFAR10 train and test splits.
+    Args:
+      cifar10_folder: Folder which contains downloaded CIFAR10 data.
+    Returns:
+      X_train: CIFAR10 train data in numpy array with shape (50000, 32, 32, 3).
[…]

### 2016-12-16 practical_3/convnet.py

@@ -23,6 +23,8 @@ class ConvNet(object):
                           output dimensions of the ConvNet.
         """
         self.n_classes = n_classes
+        self.isTrain = True
+        self.wd = 0.005
 
     def inference(self, x):
         """
@@ -57,8 +59,7 @@ class ConvNet(object):
             with tf.variable_scope('conv1') as scope:
                 w_conv1 = tf.get_variable('weights',
                                           shape=[5, 5, 3, 64],
-                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001),
-                                          regularizer=regularizers.l2_regularizer(0.001))
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
                 b_conv1 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
 
@@ -69,8 +70,7 @@ class ConvNet(object):
             with tf.variable_scope('conv2') as scope:
                 w_conv2 = tf.get_variable('weights',
                                           shape=[5, 5, 64, 64],
-                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001),
-                                          regularizer=regularizers.l2_regularizer(0.001))
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
                 b_conv2 = tf.get_variable('biases', shape=[64], initializer=tf.constant_initializer(0.0))
 
@@ -87,30 +87,41 @@ class ConvNet(object):
             with tf.variable_scope('fc1') as scope:
                 w_fc1 = tf.get_variable('weights',
                                         shape=[flatten.get_shape()[1], 384],
-                                        initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001),
-                                        regularizer=regularizers.l2_regularizer(0.001))
+                                        initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
+
+                # if self.wd is not None:
+                #     weight_decay = tf.mul(tf.nn.l2_loss(w_fc1), self.wd, name='weight_loss')
+                #     tf.add_to_collection('losses', weight_decay)
 
                 b_fc1 = tf.get_variable('biases', shape=[384], initializer=tf.constant_initializer(0.0))
 
[…]

### 2016-12-16 practical_3/retrain_vgg.py

@@ -72,7 +72,64 @@ def train():
     ########################
     # PUT YOUR CODE HERE  #
     ########################
-    raise NotImplementedError
+    model = vgg()
+
+    model.wd = None
+
+    x = tf.placeholder(tf.float32, shape=[None, 32, 32, 3])
+    y_ = tf.placeholder(tf.float32, shape=[None, 10])
+
+    x_ = model.inference(x)
+
+    with tf.name_scope('loss'):
+        loss = model.loss(x_, y_)
+
+    with tf.name_scope('accuracy'):
+        accuracy = model.accuracy(x_, y_)
+
+    with tf.name_scope('train'):
+        train_step = tf.train.AdamOptimizer(LEARNING_RATE_DEFAULT).minimize(loss)
+
+    # init = tf.initialize_all_variables()
+    # session = tf.Session()
+    # session.run(init)
+    #
+    # tf.scalar_summary('accuracy', accuracy)
+    # tf.scalar_summary('loss', loss)
+    # merged = tf.merge_all_summaries()
+    #
+    # train_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/linear-train', session.graph)
+    # test_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/linear-test', session.graph)
+    #
+    # saver = tf.train.Saver(tf.all_variables())
+    #
+    # for iteration in range(1, MAX_STEPS_DEFAULT + 1):
+    #     model.isTrain = True
+    #     batch_x, batch_y = cifar10.train.next_batch(BATCH_SIZE_DEFAULT)
+    #     _, summary = session.run([train_step, merged], feed_dict={x: batch_x, y_: batch_y})
+    #     train_writer.add_summary(summary, iteration)
+    #
+    #     if iteration % CHECKPOINT_FREQ_DEFAULT == 0:
+    #         saver.save(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(iteration) + ".ckpt")
+    #
+    #     if iteration % EVAL_FREQ_DEFAULT == 0.0:
+    #         _split = 250
+    #         avg_loss, avg_acc = 0.0, 0.0
+    #         model.isTrain = False
+    #         for _iter in range(int(len(cifar10.test.images) / _split)):
+    #             batch_x, batch_y = cifar10.test.images[_iter * _split:((_iter + 1) * _split)], \
+    #                                cifar10.test.labels[_iter * _split:((_iter + 1) * _split)]
+    #
[…]

### 2016-12-16 practical_3/siamese.py

@@ -133,12 +133,20 @@ class Siamese(object):
         ########################
         # PUT YOUR CODE HERE  #
         ########################
-        l2_dist = tf.sqrt(tf.reduce_sum(tf.square(channel_1 - channel_2)))
-        contrast = tf.maximum(0.0, margin - l2_dist)
-        loss = tf.reduce_sum(label * l2_dist + (1.0 - label) * contrast)
+        # l2_dist = tf.sqrt(tf.reduce_sum(tf.square(channel_1 - channel_2)))
+        # contrast = tf.maximum(0.0, margin - l2_dist)
+        # loss = tf.reduce_sum(label * 0.5 * l2_dist + (1.0 - label) * contrast)
 
-        # reg_loss = tf.reduce_sum(tf.get_collection(tf.GraphKeys.REGULARIZATION_LOSSES))
-        # loss += reg_loss
+        d = tf.reduce_sum(tf.square(tf.sub(channel_1, channel_2)), reduction_indices=1)
+        d = tf.sqrt(d + 1e-7)
+        loss = tf.reduce_mean(label * d + (1 - label) * tf.maximum(margin - d, 0.0))
+
+        # plain. loss = tf.reduce_mean(label * 0.5 * d + (1 - label) * tf.maximum(margin - d, 0.0)) / old sampling
+        # 1. loss = tf.reduce_mean(label * d + (1 - label) * tf.maximum(margin - d, 0.0)) / old sampling
+        # 3. loss = tf.reduce_mean(label * d + (1 - label) * tf.maximum(margin - d, 0.0)) / new sampling
+
+        # reg_losses = tf.reduce_sum(tf.get_collection(tf.GraphKeys.REGULARIZATION_LOSSES))
+        # loss += 0.01 * reg_losses
         ########################
         # END OF YOUR CODE    #
         ########################

### 2016-12-16 practical_3/train_model.py

@@ -21,19 +21,19 @@ import cifar10_siamese_utils
 LEARNING_RATE_DEFAULT = 1e-4
 BATCH_SIZE_DEFAULT = 128
 MAX_STEPS_DEFAULT = 15000
-EVAL_FREQ_DEFAULT = 1000
-CHECKPOINT_FREQ_DEFAULT = 5000
-PRINT_FREQ_DEFAULT = 10
+EVAL_FREQ_DEFAULT = 5000
+CHECKPOINT_FREQ_DEFAULT = 10000
+PRINT_FREQ_DEFAULT = 1000
 OPTIMIZER_DEFAULT = 'ADAM'
 
 DATA_DIR_DEFAULT = './cifar10/cifar-10-batches-py'
-LOG_DIR_DEFAULT = './logs/cifar10'
-CHECKPOINT_DIR_DEFAULT = './checkpoints'
+EXPERIMENT = '/' + 'linear-64-reg-.01'
+LOG_DIR_DEFAULT = './logs/cifar10' + EXPERIMENT
+CHECKPOINT_DIR_DEFAULT = './checkpoints' + EXPERIMENT
 
 cifar10 = cifar10_utils.get_cifar10(DATA_DIR_DEFAULT)
 
-cifar10_siamese = cifar10_siamese_utils.get_cifar10(DATA_DIR_DEFAULT,
-                                                     one_hot=False)
+cifar10_siamese = cifar10_siamese_utils.get_cifar10(DATA_DIR_DEFAULT, one_hot=False)
 
 def train_step(loss):
     """
@@ -97,6 +97,8 @@ def train():
     ########################
     model = ConvNet()
 
+    model.wd = None
+
     x = tf.placeholder(tf.float32, shape=[None, 32, 32, 3])
     y_ = tf.placeholder(tf.float32, shape=[None, 10])
 
@@ -117,7 +119,6 @@ def train():
 
     tf.scalar_summary('accuracy', accuracy)
     tf.scalar_summary('loss', loss)
-    tf.histogram_summary('logits', x_)
     merged = tf.merge_all_summaries()
 
     train_writer = tf.train.SummaryWriter(LOG_DIR_DEFAULT + '/linear-train', session.graph)
@@ -126,8 +127,9 @@ def train():
     saver = tf.train.Saver(tf.all_variables())
 
     for iteration in range(1, MAX_STEPS_DEFAULT+1):
+        model.isTrain = True
[…]

### 2016-12-16 practical_3/report/report_methenitis.tex
updated with transfer learning

@@
 \subsection{One-vs-Rest Classifier}
+Here, I present the accuracy of the one-vs-rest classifier on the features learned from in the final layer of the siamese network for all experiments
 \begin{itemize}
-\textbf{Experiment 1}: $0.476$
-\textbf{Experiment 2}: $0.473$
-\textbf{Experiment 3}: $0.682$
+\item \textbf{Experiment 1}: $0.476$
+\item \textbf{Experiment 2}: $0.473$
+\item \textbf{Experiment 3}: $\mathbf{0.682}$
 \end{itemize}
 
-%Figure~\ref{fig:6} illustrates the loss in the training and the test set using the normal implementation of the batch creation.
-%The siamese network learning converges after $12000$ steps.
-%The network seems to learn the features that minimize the loss.
-%Figure~\ref{fig:7} presents four different implementations using different parameters.
+\section{Transfer Learning}
+
+ \begin{figure}[h!]
+\centering
+\includegraphics[width=5.2cm]{graph.png}
+\caption{Graph for the task 3 of the assignment, the final three layers of convnet were used. Note the stop gradient operation, where we don't want to update the pre-trained weights.}
+\label{fig:features}
+\end{figure}
+
 %
-%
-%\begin{figure}[h!]
-%\centering
-%\includegraphics[width=7.2cm]{loss-siamese-train-1.png}\	
-%\includegraphics[width=6.6cm]{loss-siamese-test-1.pdf}
-%\caption{Loss in the training (Left) and the test set (Right - green line) for $15000$ training steps, $margin = 0.2$, and weight regularization loss.}
-%\label{fig:6}
-%\end{figure}
-%
-%
-%\begin{figure}[h!]
-%\centering
-%\includegraphics[width=0.4\textwidth]{loss-siamese-train-1}
-%\includegraphics[width=0.4\textwidth]{loss-siamese-train-2}
-%\includegraphics[width=0.4\textwidth]{loss-siamese-train-3}
-%\includegraphics[width=0.4\textwidth]{loss-siamese-train-4}
-%\caption{Visualization of the $l2$-normalized features in the output of the CNN for $5000$ samples of the test set.
-For $margin=0.2$ with weight normalization (top-left), for $margin=1.0$ with weight normalization (top-right), and without normalization (bottom-left).
-Last, the visualization of the features when the alternative way of creating batches is used (bottom-right).
-%For $margin=1.0$ the alternative way of creating batches is reducing the loss.}
-%\label{fig:7}
-%\end{figure}
-%
-%
-%\subsection{Feature Visualization}
-%
-%
-%Using the same TSNE algorithm we present the $2$-dimensional representation of the features for the siamese architecture.
-Figure~\ref{fig:8} presents the $2$-d representation of the features over $5000$ samples of the test set, for the four different implementation showed in Figure~\ref{fig:7}.
-%
-%\begin{figure}[h!]
-%\centering
-%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2.pdf}
-%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2-1.pdf}
-%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2-2.pdf}
-%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2-3.pdf}
-%\caption{Visualization of the $l2$-normalized features in the output of the CNN for $5000$ samples of the test set.
-For $margin=0.2$ with weight normalization (top-left), for $margin=1.0$ with weight normalization (top-right), and without normalization (bottom-left).
-Last, the visualization of the features when the alternative way of creating batches is used $margin = 1.0$ and without weight normalization (bottom-right).}
-%\label{fig:8}
-%\end{figure}
-%
-%\subsection{One-vs-All Classifiers}
-%
-%For the four different implementation parameters that were presented in the Figure~\ref{fig:7} and \ref{fig:8} the accuracy of the one-vs-all classifier that is achieved:
-%\begin{itemize}
-%\item Accuracy with l\_2-norm: $0.0957$
-%\item Accuracy with l\_2-norm: $0.121$
-%\item Accuracy with l\_2-norm: $0.1048$
-%\item Accuracy with l\_2-norm: $0.1564$
-%\end{itemize}
-%I showed that the loss was reduced by using the alternative way of sampling batches, here the accuracy of the classifier is increased as well.
-%Figure
-%
-%
-%\subsection{Update for Task 2}
-%
-%In this section I provide the results of a last experiment where I used $50000$ training steps.
-%The model seems to learn and distinguishes between different classes.
-%Figure~\ref{fig:9} presents the loss in the training set.
-%
-%
-%
-%\begin{figure}[h!]
-%\centering
-%\includegraphics[width=0.8\textwidth]{loss-siamese-final.png}
-%\caption{Loss of the siamese architecture of the CNN in the training procedure for $50000$ training steps. For $margin=1.0$ without weight normalization.}
-%\label{fig:9}
-%\end{figure}
-%
-%Figure~\ref{fig:10} presents the visualized in $2-d$ features.
-%
-%\begin{figure}[h!]
-%\centering
-%\includegraphics[width=0.8\textwidth]{visualization-siamese-features_fc2-4.pdf}
-%\caption{Visualization of the $l2$-normalized features in the output of the CNN for all samples of the test set. For $margin=1.0$ without weight normalization.}
-%\label{fig:10}
-%\end{figure}
-%
-%To test the accuracy of the one-vs-all classifier I use the features retained by the learned model to train the classifiers.
-%Using the 80 percent of the features I train a linear kernel OneVsRest classifier, and test the accuracy over the rest 20 percent.
-%The reported accuracy over the test set is:
-%\begin{itemize}
-%\item Accuracy with l\_2-norm: $0.6789$
-%\end{itemize}
-%
-%
-%
+%Using the same TSNE algorithm we present the $2$-dimensional representation of the feat
 %\section{Conclusion}

### 2016-12-16 practical_3/convnet.py

@@ -56,6 +56,9 @@ class ConvNet(object):
             ########################
             # PUT YOUR CODE HERE  #
             ########################
+            '''
+                For linear
+            '''
             with tf.variable_scope('conv1') as scope:
                 w_conv1 = tf.get_variable('weights',
                                           shape=[5, 5, 3, 64],
@@ -83,7 +86,6 @@ class ConvNet(object):
                                                      int(h_pool2.get_shape()[1] *
                                                          h_pool2.get_shape()[2] *
                                                          h_pool2.get_shape()[3])], name="h_f_flatten")
-
             with tf.variable_scope('fc1') as scope:
                 w_fc1 = tf.get_variable('weights',
                                         shape=[flatten.get_shape()[1], 384],
@@ -124,7 +126,6 @@ class ConvNet(object):
 
 
             logits = tf.matmul(h_fc2, w_fc3) + b_fc3
-
             ########################
             # END OF YOUR CODE    #
             ########################

### 2016-12-16 practical_3/retrain_vgg.py

@@ -4,22 +4,29 @@ from __future__ import print_function
 
 import argparse
 import os
+import vgg
+from convnet import ConvNet
 
 import tensorflow as tf
 import numpy as np
 
+import cifar10_utils
+
 LEARNING_RATE_DEFAULT = 1e-4
 BATCH_SIZE_DEFAULT = 128
-MAX_STEPS_DEFAULT = 15000
+MAX_STEPS_DEFAULT = 10000
 EVAL_FREQ_DEFAULT = 1000
 CHECKPOINT_FREQ_DEFAULT = 5000
 PRINT_FREQ_DEFAULT = 10
 OPTIMIZER_DEFAULT = 'ADAM'
 REFINE_AFTER_K_STEPS_DEFAULT = 0
 
+EXPERIMENT = '/' + 'vgg16-retraining'
 DATA_DIR_DEFAULT = './cifar10/cifar-10-batches-py'
-LOG_DIR_DEFAULT = './logs/cifar10'
-CHECKPOINT_DIR_DEFAULT = './checkpoints'
+LOG_DIR_DEFAULT = './logs/cifar10' + EXPERIMENT
+CHECKPOINT_DIR_DEFAULT = './checkpoints' + EXPERIMENT
+
+cifar10 = cifar10_utils.get_cifar10(DATA_DIR_DEFAULT)
 
 def train_step(loss):
     """
@@ -72,14 +79,45 @@ def train():
     ########################
     # PUT YOUR CODE HERE  #
     ########################
-    model = vgg()
+    model = ConvNet()
 
-    model.wd = None
+    vgg.load_weights(vgg.VGG_FILE)
 
     x = tf.placeholder(tf.float32, shape=[None, 32, 32, 3])
     y_ = tf.placeholder(tf.float32, shape=[None, 10])
+    refine = tf.placeholder(tf.bool)
 
-    x_ = model.inference(x)
+    pool5, assign_ops = vgg.load_pretrained_VGG16_pool5(x)
+    pool5 = tf.cond(refine, lambda : pool5, lambda : tf.stop_gradient(pool5))
+
+    with tf.variable_scope('flatten') as scope:
+        flatten = tf.reshape(pool5, shape=[-1, 512], name="h_f_flatten")
+
+    with tf.variable_scope('fc1') as scope:
+        w_fc1 = tf.get_variable('weights',
+                                shape=[flatten.get_shape()[1], 384],
[…]

### 2016-12-16 practical_3/train_model.py

@@ -296,63 +296,63 @@ def feature_extraction():
             saver = tf.train.Saver(tf.all_variables())
             saver.restore(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(MAX_STEPS_DEFAULT) + ".ckpt")
 
-            batch_x, batch_y = cifar10.test.images[:500], cifar10.test.labels[:500]
+            batch_x, batch_y = cifar10.test.images, cifar10.test.labels
             x_, features_flatten, features_fc1, features_fc2 = session.run([x_, features_flatten, features_fc1, features_fc2], feed_dict={x: batch_x, y_: batch_y})
 
-            '''
-            VISUALIZATION
-            '''
-            if 0:
-                tsne = TSNE(n_components=2, verbose=1, perplexity=40, n_iter=300)
-                tsne_result = tsne.fit_transform(features_flatten)
-                plt.figure()
-                colors = cm.rainbow(np.linspace(0, 1, len(batch_y[0])))
-                sizes = np.random.random_integers(25, 50, size=len(batch_y[0]))
-                for i in range(len(batch_y[0])):
-                    index = np.where(np.argmax(batch_y, axis=1) == i)
-                    plt.scatter(tsne_result[index,0], tsne_result[index, 1], c=colors[i], s=sizes[i], label=i)
-                plt.legend(numpoints=1, fontsize=8)
-                plt.savefig("visualization-linear-features_flatten.pdf", bbox_inches = 'tight')
+        '''
+        VISUALIZATION
+        '''
+        if 0:
+            tsne = TSNE(n_components=2, verbose=1, perplexity=40, n_iter=300)
+            tsne_result = tsne.fit_transform(features_flatten)
+            plt.figure()
+            colors = cm.rainbow(np.linspace(0, 1, len(batch_y[0])))
+            sizes = np.random.random_integers(25, 50, size=len(batch_y[0]))
+            for i in range(len(batch_y[0])):
+                index = np.where(np.argmax(batch_y, axis=1) == i)
+                plt.scatter(tsne_result[index,0], tsne_result[index, 1], c=colors[i], s=sizes[i], label=i)
+            plt.legend(numpoints=1, fontsize=8)
+            plt.savefig("visualization-linear-features_flatten.pdf", bbox_inches = 'tight')
 
-                tsne = TSNE(n_components=2, verbose=1, perplexity=40, n_iter=300)
-                tsne_result = tsne.fit_transform(features_fc1)
-                plt.figure()
[…]

### 2016-12-16 practical_3/vgg.py

@@ -276,6 +276,7 @@ def load_pretrained_VGG16_pool5(input, scope_name='vgg'):
     return pool5, assign_ops
 
 def load_weights(weight_file):
+  print("Loading Weights")
   weights = np.load(weight_file)
   keys = sorted(weights.keys())
   return weights, keys

### 2016-12-16 practical_3/report/report_methenitis.tex
update report

@@
 \end{verbatim}
-Here, the reported accuracy of the one-vs-classifiers on the test set:
+Here, the reported accuracy\footnote{The accuracy is reported to half of the test set ($5000$ random samples without replacement due to slow training of the OneVsRestClassifier		)} of the one-vs-classifiers on the test set:
 \begin{itemize}
-\item Accuracy with flatten features: $0.6306$.
-\item Accuracy with fc1 features: $0.$.
-\item Accuracy with fc2 features: $0.$.
+\item Accuracy with flatten features: $0.59$.
+\item Accuracy with fc1 features: $0.59$.
+\item Accuracy with fc2 features: $0.703$.
 \end{itemize}
@@
 \end{verbatim}
+Is is expected that classes are uniformly picked in expectation given the random sampling. Given the default way of selecting training batches training among classes is not guarranteed to be uniform.
+Later we see that the alternative way of creating batches achieves the highest accuracy in the end of training using the one-vs-rest classifier.
 \end{itemize}
@@
 \caption{Graph for the task 3 of the assignment, the final three layers of convnet were used. Note the stop gradient operation, where we don't want to update the pre-trained weights.}
-\label{fig:features}
+\label{fig:graph}
 \end{figure}
+
+\subsection{Feature Extraction}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=12.2cm]{acc-transfer.png}\	
+\includegraphics[width=12.2cm]{loss-transfer.png}
+\caption{}
+\label{fig:extra}
+\end{figure}
+
+\subsection{Retraining}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=12.2cm]{acc-retrain.png}\	
+\includegraphics[width=12.2cm]{loss-retrain.png}
+\caption{}
+\label{fig:retrain}
+\end{figure}
+
+\subsubsection{Refining}
 

### 2016-12-16 practical_3/convnet.py

@@ -91,30 +91,30 @@ class ConvNet(object):
                                         shape=[flatten.get_shape()[1], 384],
                                         initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                # if self.wd is not None:
-                #     weight_decay = tf.mul(tf.nn.l2_loss(w_fc1), self.wd, name='weight_loss')
-                #     tf.add_to_collection('losses', weight_decay)
+                if self.wd is not None:
+                    weight_decay = tf.mul(tf.nn.l2_loss(w_fc1), self.wd, name='weight_loss')
+                    tf.add_to_collection('losses', weight_decay)
 
                 b_fc1 = tf.get_variable('biases', shape=[384], initializer=tf.constant_initializer(0.0))
 
                 h_fc1 = tf.nn.relu(tf.matmul(flatten, w_fc1) + b_fc1, name="h_f_fc1")
 
-                # h_fc1 = tf.cond(tf.cast(self.isTrain, tf.bool), lambda: tf.nn.dropout(h_fc1, 0.8), lambda: h_fc1)
+                h_fc1 = tf.cond(tf.cast(self.isTrain, tf.bool), lambda: tf.nn.dropout(h_fc1, 0.8), lambda: h_fc1)
 
             with tf.variable_scope('fc2') as scope:
                 w_fc2 = tf.get_variable('weights',
                                         shape=[384, 192],
                                         initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                # if self.wd is not None:
-                #     weight_decay = tf.mul(tf.nn.l2_loss(w_fc2), self.wd, name='weight_loss')
-                #     tf.add_to_collection('losses', weight_decay)
+                if self.wd is not None:
+                    weight_decay = tf.mul(tf.nn.l2_loss(w_fc2), self.wd, name='weight_loss')
+                    tf.add_to_collection('losses', weight_decay)
 
                 b_fc2 = tf.get_variable('biases', shape=[192], initializer=tf.constant_initializer(0.0))
 
                 h_fc2 = tf.nn.relu(tf.matmul(h_fc1, w_fc2) + b_fc2, name="h_f_fc2")
 
-                # h_fc2 = tf.cond(tf.cast(self.isTrain, tf.bool), lambda : tf.nn.dropout(h_fc2, 0.), lambda : h_fc2)
[…]

### 2016-12-16 practical_3/retrain_vgg.py

@@ -19,9 +19,9 @@ EVAL_FREQ_DEFAULT = 1000
 CHECKPOINT_FREQ_DEFAULT = 5000
 PRINT_FREQ_DEFAULT = 10
 OPTIMIZER_DEFAULT = 'ADAM'
-REFINE_AFTER_K_STEPS_DEFAULT = 0
+REFINE_AFTER_K_STEPS_DEFAULT = 100
 
-EXPERIMENT = '/' + 'vgg16-retraining'
+EXPERIMENT = '/' + 'vgg16-refine-100'
 DATA_DIR_DEFAULT = './cifar10/cifar-10-batches-py'
 LOG_DIR_DEFAULT = './logs/cifar10' + EXPERIMENT
 CHECKPOINT_DIR_DEFAULT = './checkpoints' + EXPERIMENT
@@ -90,6 +90,10 @@ def train():
     pool5, assign_ops = vgg.load_pretrained_VGG16_pool5(x)
     pool5 = tf.cond(refine, lambda : pool5, lambda : tf.stop_gradient(pool5))
 
+
+    #############
+    ## Extra layers
+    #############
     with tf.variable_scope('flatten') as scope:
         flatten = tf.reshape(pool5, shape=[-1, 512], name="h_f_flatten")
 
@@ -117,6 +121,10 @@ def train():
 
         b_fc3 = tf.get_variable('biases', shape=[10], initializer=tf.constant_initializer(0.0))
 
+    #############
+    ## Extra layers
+    #############
+
     x_ = tf.matmul(h_fc2, w_fc3) + b_fc3
 
     with tf.name_scope('loss'):
@@ -132,6 +140,7 @@ def train():
     session = tf.Session()
     session.run(init)
 
+    # Assign ops for weight restoration
     session.run(assign_ops)
 
     tf.scalar_summary('accuracy', accuracy)
@@ -152,12 +161,10 @@ def train():
 
         train_writer.add_summary(summary, iteration)
 
-        print(iteration, acc, l)
-
         if iteration % CHECKPOINT_FREQ_DEFAULT == 0:
             saver.save(session, CHECKPOINT_DIR_DEFAULT + "/linear-model-at-" + str(iteration) + ".ckpt")
 
-        if iteration % EVAL_FREQ_DEFAULT == 0.0:
+        if iteration % EVAL_FREQ_DEFAULT == 0.0 or iteration == 1:
             _split = 250
             avg_loss, avg_acc = 0.0, 0.0
             model.isTrain = False

### 2016-12-16 practical_3/report/report_methenitis.tex
update report

@@
 \subsection{Feature Visualization}
+\label{sec:vis}
 
@@
 \begin{itemize}
-\item Accuracy with flatten features: $0.59$.
+\item Accuracy with flatten features: $0.6305$.
 \item Accuracy with fc1 features: $0.59$.
-\item Accuracy with fc2 features: $0.703$.
+\item Accuracy with fc2 features: $\mathbf{0.7685}$.
 \end{itemize}
@@
 \end{enumerate}
+In the first the distance in similar label images is multiplied by half, while in the second is not.
 
@@
 
+I construct 3 experiments using both the \texttt{next\_batch} ways (default \& alternative) and the two loss functions.
+\begin{description}
+\item[Experiment 1]{Using the loss function (1) and the default creation of batches}
+\item[Experiment 2]{Using the loss function (2) and the default creation of batches}
+\item[Experiment 3]{Using the loss function (2) and the alternative creation of batches}
+\end{description}
+Figure~\ref{fig:siamese} presents the loss in the training and the test set for $50000$ training steps for the setting of the experiment 1.
+Loss in the test set is computed every $1000$ steps.
+We see that the loss in the training set in decreasing as the training steps increase.
+The same occurs for the loss in the test set.
 \begin{figure}[h!]
@@
 \end{figure}
-
+Figure~\ref{fig:siamese-1} presents the loss in the training and the test set for $50000$ training steps for the setting of the experiment 2.
+Here the scaling of the loss is different as a result of the different loss function used in experiment 2.
 \begin{figure}[h!]
@@
 \includegraphics[width=10.2cm]{siamese-1.png}
-\caption{\textbf{Experiment 2} Loss in the training (blue line) and the test set (light purple line) for $50000$ training steps, $margin = 1.0$, using the default \texttt{next\_batch} method and the loss function (2).
+\caption{\textbf{Experiment 2} (Different Loss Functions) Loss in the training (blue line) and the test set (light purple line) for $50000$ training steps, $margin = 1.0$, using the default \texttt{next\_batch} method and the loss function (2).
 Loss in the training (purple line) and the test set (yellow line) for $50000$ training steps, $margin = 1.0$, using the default \texttt{next\_batch} method and the loss function (1).}
@@
 \end{figure}
-
+Figure~\ref{fig:siamese-2} presents the loss in the training and the test set for $50000$ training steps for the setting of the experiment 3.
+Here I compare between two different ways of batch sampling between experiment 2 and 3.
+The same loss function in used both experiments.
+It is easy to see that using the alternative batch sampling, the loss is decreasing faster and results in lower loss in the test set as well.
+In the next section I show that the features retained with the alternative batch sampling increase the accuracy of the one-vs-rest classifier.
 \begin{figure}[h!]
@@
 \includegraphics[width=10.2cm]{siamese-2.png}
-\caption{\textbf{Experiment 3} Loss in the training (blue line) and the test set (light purple line) for $50000$ training steps, $margin = 1.0$, using the default \texttt{next\_batch} method and the loss function (2).
+\caption{\textbf{Experiment 3} (Default vs Alternative Batch Creation) Loss in the training (blue line) and the test set (light purple line) for $50000$ training steps, $margin = 1.0$, using the default \texttt{next\_batch} method and the loss function (2).
 Loss in the training (yellow line) and the test set (light purple line) for $50000$ training steps, $margin = 1.0$, using the default \texttt{next\_batch} method and the loss function (2).}
@@
 
+In the previous section I set up three experiments and presented the loss during training in the training set.
+In this section I illustrate the features in the 2-dimensional space as these transformed by TSNE (as this was implemented in Section~\ref{sec:vis}.).
+
 \begin{figure}[h!]
@@
 \includegraphics[width=7.2cm]{visualization-siamese-3.pdf}
-\caption{}
+\caption{Visualization of the $2D$ features generated out of the whole test set. Experiment 1 (top left), experiment 2 (top right), experiment 3 (bottom).}
 \label{fig:features}
@@
 \subsection{One-vs-Rest Classifier}
-Here, I present the accuracy of the one-vs-rest classifier on the features learned from in the final layer of the siamese network for all experiments
+
+Here, I present the accuracy of the one-vs-rest classifier on the features learned from in the final layer of the siamese network for all experiments.
+
 \begin{itemize}
@@
 
-\section{Transfer Learning}
+Using the different loss function with the default batch sampling method did not help the accuracy obtained.
+However, in experiment 3 I used the alternative batch sampling function which was the main reason for the large improvement in the accuracy.
+
+\clearpage
+
+\section{Task 3: Transfer Learning}
 
@@
 \subsection{Feature Extraction}
+
+In this section I present the results of my implementation for the feature extraction of the third task.
+I used the last 3 layers of the convNet inference method from the first task of the assignment.
+I also used stopGradient method of tensorflow to disconnect vgg pretrained network from convNet and the training updates.
 
@@
 
-%
-%Using the same TSNE algorithm we present the $2$-dimensional representation of the feat
-%\section{Conclusion}
-%
-%In this assignment I implemented a CNN and reported its performance over the CIFAR10 dataset using different parameters.
-%I also implemented the siamese architecture which uses two versions of the same CNN to perform learning in order to distinguish between classes.
-%The amount of training steps requires for the siamese are higher than the single CNN architecture.
-%The time required for the experiments did not let me try more parameter values, therefore I cannot draw any important conclusions regarding the right parameters that should be used for the two different approaches.
+\subsection{Performance of transfer learning on Cifar10}
+\begin{description}
+\item[Feature extraction:]{$0.6743$}
+\item[Retraining:]{$0.8505$}
+\item[Refining-$100$:]{$0.8441$}
+\item[Refining-$1000$:]{$0.8461$}
+\item[Refining-$2500$:]{$\mathbf{0.8510}$}
+\end{description}
+
+\section{Conclusion}
+
+In this assignment I implemented a CNN and reported its performance over the CIFAR10 dataset using different parameters.
+I also implemented the siamese architecture which uses two versions of the same CNN to perform learning in order to distinguish between classes.
+I showed that using the alternative batch sampling procedure the loss is reduced and the features retained result in better accuracy when an one-vs-rest classifier is used.
+The amount of training steps requires for the siamese are higher than the single CNN architecture.
+Last, I implemented the third task of the assignment where we import pre-trained layers from VGG-16 and apply learning on Cifar10 dataset.
 

### 2016-12-16 practical_3/convnet.py

@@ -91,30 +91,30 @@ class ConvNet(object):
                                         shape=[flatten.get_shape()[1], 384],
                                         initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                if self.wd is not None:
-                    weight_decay = tf.mul(tf.nn.l2_loss(w_fc1), self.wd, name='weight_loss')
-                    tf.add_to_collection('losses', weight_decay)
+                # if self.wd is not None:
+                #     weight_decay = tf.mul(tf.nn.l2_loss(w_fc1), self.wd, name='weight_loss')
+                #     tf.add_to_collection('losses', weight_decay)
 
                 b_fc1 = tf.get_variable('biases', shape=[384], initializer=tf.constant_initializer(0.0))
 
                 h_fc1 = tf.nn.relu(tf.matmul(flatten, w_fc1) + b_fc1, name="h_f_fc1")
 
-                h_fc1 = tf.cond(tf.cast(self.isTrain, tf.bool), lambda: tf.nn.dropout(h_fc1, 0.8), lambda: h_fc1)
+                # h_fc1 = tf.cond(tf.cast(self.isTrain, tf.bool), lambda: tf.nn.dropout(h_fc1, 0.8), lambda: h_fc1)
 
             with tf.variable_scope('fc2') as scope:
                 w_fc2 = tf.get_variable('weights',
                                         shape=[384, 192],
                                         initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001))
 
-                if self.wd is not None:
-                    weight_decay = tf.mul(tf.nn.l2_loss(w_fc2), self.wd, name='weight_loss')
-                    tf.add_to_collection('losses', weight_decay)
+                # if self.wd is not None:
+                #     weight_decay = tf.mul(tf.nn.l2_loss(w_fc2), self.wd, name='weight_loss')
+                #     tf.add_to_collection('losses', weight_decay)
 
                 b_fc2 = tf.get_variable('biases', shape=[192], initializer=tf.constant_initializer(0.0))
 
                 h_fc2 = tf.nn.relu(tf.matmul(h_fc1, w_fc2) + b_fc2, name="h_f_fc2")
 
-                h_fc2 = tf.cond(tf.cast(self.isTrain, tf.bool), lambda : tf.nn.dropout(h_fc2, 0.), lambda : h_fc2)
[…]

### 2016-12-16 practical_3/train_model.py

@@ -339,20 +339,20 @@ def feature_extraction():
             train_set = range(int(features_flatten.shape[0]*0.8))
             test_set = range(train_set[-1]+1, features_flatten.shape[0])
 
-            classif = OneVsRestClassifier(SVC(kernel='linear'))
-            classif.fit(features_flatten[train_set], np.argmax(batch_y[train_set], axis=1))
-            print("Accuracy with flatten:",
-                  classif.score(features_flatten[test_set], np.argmax(batch_y[test_set], axis=1)))
-
-            classif = OneVsRestClassifier(SVC(kernel='linear'))
+            # classif = OneVsRestClassifier(SVC(kernel='linear'))
+            # classif.fit(features_flatten[train_set], np.argmax(batch_y[train_set], axis=1))
+            # print("Accuracy with flatten:",
+            #       classif.score(features_flatten[test_set], np.argmax(batch_y[test_set], axis=1)))
+            #
+            classif = OneVsRestClassifier(SVC(kernel='linear'), n_jobs=8)
             classif.fit(features_fc1[train_set], np.argmax(batch_y[train_set], axis=1))
             print("Accuracy with features_fc1:",
                   classif.score(features_fc1[test_set], np.argmax(batch_y[test_set], axis=1)))
 
-            classif = OneVsRestClassifier(SVC(kernel='linear'))
-            classif.fit(features_fc2[train_set], np.argmax(batch_y[train_set], axis=1))
-            print("Accuracy with features_fc2:",
-                  classif.score(features_fc2[test_set], np.argmax(batch_y[test_set], axis=1)))
+            # classif = OneVsRestClassifier(SVC(kernel='linear'), n_jobs=8)
+            # classif.fit(features_fc2[train_set], np.argmax(batch_y[train_set], axis=1))
+            # print("Accuracy with features_fc2:",
+            #       classif.score(features_fc2[test_set], np.argmax(batch_y[test_set], axis=1)))
 
     elif FLAGS.train_model == 'siamese':
 

### 2016-12-16 practical_3/report/report_methenitis.tex
final submission

@@
 \subsubsection{Dropout}
+Figure~\ref{fig:6} illustrates the results with dropout enables for values $0.2, 0.5$.
 
@@
 \end{verbatim}
-Here, the reported accuracy\footnote{The accuracy is reported to half of the test set ($5000$ random samples without replacement due to slow training of the OneVsRestClassifier		)} of the one-vs-classifiers on the test set:
+Here, the reported accuracy of the one-vs-classifiers on the test set:
 \begin{itemize}
 \item Accuracy with flatten features: $0.6305$.
-\item Accuracy with fc1 features: $0.59$.
+\item Accuracy with fc1 features: $0.7465$.
 \item Accuracy with fc2 features: $\mathbf{0.7685}$.
@@
 It is natural that the accuracy is higher for later layers.
-As it was earlier $fc2$ layer can distinguish better features of different classes.
+As it was earlier shown $fc2$ layer can generates features that the one-cs-rest classifier can distinguish different classes easier than from the other layers.
 
@@
 In the previous section I set up three experiments and presented the loss during training in the training set.
-In this section I illustrate the features in the 2-dimensional space as these transformed by TSNE (as this was implemented in Section~\ref{sec:vis}.).
+In this section I illustrate the features in the 2-dimensional space as these transformed by TSNE (as this was implemented in Section~\ref{sec:vis}).
+Figure~\ref{fig:features} presents the features generated by the normalized output layer of the network for the setting used in the 3 experiments.
 
@@
 I also used stopGradient method of tensorflow to disconnect vgg pretrained network from convNet and the training updates.
+Figure~\ref{fig:extra} illustrates the performance on the training and the test set for $10000$ training steps.
+The accuracy, when updating only the last three layers of the network, approximates $0.67$ which is lower than the performance of the network in task 1.
+It shows that features obtained by another pretrained network cannot work that well in an another task.
 
@@
 \includegraphics[width=12.2cm]{loss-transfer.png}
-\caption{}
+\caption{(Feature extraction) Accuracy and loss in the training (purple line) and the test set (yellow line) for $10000$ training step.}
 \label{fig:extra}
@@
 
+Here I present the results of retraining, stop gradient is disabled and thus all the weights are updated from the beginning of the training procedure.
+Figure~\ref{fig:retrain} illustrates the performance on the training and the test set for $10000$ training steps.
+The accuracy approximates $0.85$ which is $9\%$ higher than the best performance achieved in task 1 of the assignment.
+Which is a natural result given that weights are initialized with ``good'' priors.
+
 \begin{figure}[h!]
@@
 \includegraphics[width=12.2cm]{loss-retrain.png}
-\caption{}
+\caption{(Retraining) Accuracy and loss in the training (orange line) and the test set (brown line) for $10000$ training step.}
 \label{fig:retrain}
@@
 
+Here I present the results of refining, stop gradient is disabled after $k$-training steps and thus all the weights are updated only after $k$-step during training.
+Figure~\ref{fig:refine} illustrates the performance on the training and the test set for $10000$ training steps.
+The accuracy approximates $0.85$ which is equivalent to the performance achieved in the retraining task.
+Note, the big drops in accuracy and jumps in loss after the refining starting step.
+This is due to the heavy influence the initial layers of the VGG have on the classification, where small changes in the weights influence a lot the output of the network.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=12.2cm]{acc-refine.png}\	
+\includegraphics[width=12.2cm]{loss-refine.png}
+\caption{(Refining) Accuracy and loss in the training (orange line) and the test set (blue line) for $10000$ training step, refining after $100$ training steps.
+Accuracy and loss in the training (purple line) and the test set (cyan line) for $10000$ training step, refining after $1000$ training steps.
+Accuracy and loss in the training (green line) and the test set (blue line) for $10000$ training step, refining after $2500$ training steps.}
+\label{fig:refine}
+\end{figure}
+
 \subsection{Performance of transfer learning on Cifar10}
+
+Here I present the results on the test set after $10000$ training steps of all the methods studied above.
 \begin{description}
@@
 \end{description}
+The highest performance was achieved by refining-$2500$ where the weights of the pre-trained network started to be optimized for the Cifar10 task after $2500$ training steps.
+However, the performance was approximately equivalent to the retraining method, where all weights are updated during the whole period of training.
 

### 2016-12-16 practical_3/methenitis_assignment_3/cifar10_siamese_utils.py

@@ -1,0 +1,373 @@
+"""
+This module implements utility functions for downloading and reading CIFAR10 data.
+You don't need to change anything here.
+"""
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import numpy as np
+import os
+import cPickle as pickle
+
+from six.moves import xrange
+
+import random
+from tensorflow.contrib.learn.python.learn.datasets import base
+
+# Default paths for downloading CIFAR10 data
+CIFAR10_FOLDER = 'cifar10/cifar-10-batches-py'
+
+
+def load_cifar10_batch(batch_filename):
+    """
+    Loads single batch of CIFAR10 data.
+    Args:
+      batch_filename: Filename of batch to get data from.
+    Returns:
+      X: CIFAR10 batch data in numpy array with shape (10000, 32, 32, 3).
+      Y: CIFAR10 batch labels in numpy array with shape (10000, ).
+    """
+    with open(batch_filename, 'rb') as f:
+        batch = pickle.load(f)
+        X = batch['data']
+        Y = batch['labels']
+        X = X.reshape(10000, 3, 32, 32).transpose(0, 2, 3, 1).astype(np.float32)
+        Y = np.array(Y)
+        return X, Y
+
+
+def load_cifar10(cifar10_folder):
+    """
+    Loads CIFAR10 train and test splits.
+    Args:
+      cifar10_folder: Folder which contains downloaded CIFAR10 data.
+    Returns:
+      X_train: CIFAR10 train data in numpy array with shape (50000, 32, 32, 3).
+      Y_train: CIFAR10 train labels in numpy array with shape (50000, ).
+      X_test: CIFAR10 test data in numpy array with shape (10000, 32, 32, 3).
+      Y_test: CIFAR10 test labels in numpy array with shape (10000, ).
+
+    """
+    Xs = []
+    Ys = []
+    for b in range(1, 6):
+        batch_filename = os.path.join(cifar10_folder, 'data_batch_' + str(b))
+        X, Y = load_cifar10_batch(batch_filename)
+        Xs.append(X)
+        Ys.append(Y)
+    X_train = np.concatenate(Xs)
+    Y_train = np.concatenate(Ys)
+    X_test, Y_test = load_cifar10_batch(os.path.join(cifar10_folder, 'test_batch'))
+    return X_train, Y_train, X_test, Y_test
+
+
[…]

### 2016-12-16 practical_3/methenitis_assignment_3/retrain_vgg.py

@@ -1,0 +1,245 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import argparse
+import os
+import vgg
+from convnet import ConvNet
+
+import tensorflow as tf
+import numpy as np
+
+import cifar10_utils
+
+LEARNING_RATE_DEFAULT = 1e-4
+BATCH_SIZE_DEFAULT = 128
+MAX_STEPS_DEFAULT = 10000
+EVAL_FREQ_DEFAULT = 1000
+CHECKPOINT_FREQ_DEFAULT = 5000
+PRINT_FREQ_DEFAULT = 10
+OPTIMIZER_DEFAULT = 'ADAM'
+REFINE_AFTER_K_STEPS_DEFAULT = 100
+
+EXPERIMENT = '/' + 'vgg16-refine-100'
+DATA_DIR_DEFAULT = './cifar10/cifar-10-batches-py'
+LOG_DIR_DEFAULT = './logs/cifar10' + EXPERIMENT
+CHECKPOINT_DIR_DEFAULT = './checkpoints' + EXPERIMENT
+
+cifar10 = cifar10_utils.get_cifar10(DATA_DIR_DEFAULT)
+
+def train_step(loss):
+    """
+    Defines the ops to conduct an optimization step. You can set a learning
+    rate scheduler or pick your favorite optimizer here. This set of operations
+    should be applicable to both ConvNet() and Siamese() objects.
+
+    Args:
+        loss: scalar float Tensor, full loss = cross_entropy + reg_loss
+
+    Returns:
+        train_op: Ops for optimization.
+    """
+    ########################
+    # PUT YOUR CODE HERE  #
+    ########################
+    raise NotImplementedError
+    ########################
+    # END OF YOUR CODE    #
+    ########################
+
+    return train_op
+
+def train():
+    """
+    Performs training and evaluation of your model.
+
+    First define your graph using vgg.py with your fully connected layer.
+    Then define necessary operations such as trainer (train_step in this case),
+    savers and summarizers. Finally, initialize your model within a
+    tf.Session and do the training.
+
+    ---------------------------------
+    How often to evaluate your model:
+    ---------------------------------
+    - on training set every PRINT_FREQ iterations
+    - on test set every EVAL_FREQ iterations
+
+    ---------------------------
+    How to evaluate your model:
+    ---------------------------
+    Evaluation on test set should be conducted over full batch, i.e. 10k images,
[…]

### 2016-12-16 practical_3/methenitis_assignment_3/siamese.py

@@ -1,0 +1,153 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import tensorflow as tf
+import numpy as np
+
+from tensorflow.contrib.layers import initializers
+from tensorflow.contrib.layers import regularizers
+
+class Siamese(object):
+    """
+    This class implements a siamese convolutional neural network in
+    TensorFlow. Term siamese is used to refer to architectures which
+    incorporate two branches of convolutional networks parametrized
+    identically (i.e. weights are shared). These graphs accept two
+    input tensors and a label in general.
+    """
+
+    def inference(self, x, reuse = False):
+        """
+        Defines the model used for inference. Output of this model is fed to the
+        objective (or loss) function defined for the task.
+
+        Here we recommend you to consider using variable and name scopes in order
+        to make your graph more intelligible for later references in TensorBoard
+        and so on. You can define a name scope for the whole model or for each
+        operator group (e.g. conv+pool+relu) individually to group them by name.
+        Variable scopes are essential components in TensorFlow for parameter sharing.
+        You can use the variable scope to activate/deactivate 'variable reuse'.
+
+        Args:
+           x: 4D float Tensor of size [batch_size, input_height, input_width, input_channels]
+           reuse: Python bool to switch reusing on/off.
+
+        Returns:
+           l2_out: L2-normalized output tensor of shape [batch_size, 192]
+
+        Hint: Parameter reuse indicates whether the inference graph should use
+        parameter sharing or not. You can study how to implement parameter sharing
+        in TensorFlow from the following sources:
+
+        https://www.tensorflow.org/versions/r0.11/how_tos/variable_scope/index.html
+        """
+        with tf.variable_scope('ConvNet') as conv_scope:
+            ########################
+            # PUT YOUR CODE HERE  #
+            ########################
+            with tf.variable_scope('conv1', reuse=reuse) as scope:
+                w_conv1 = tf.get_variable('weights',
+                                          shape=[5, 5, 3, 64],
+                                          initializer=tf.random_normal_initializer(mean=0.0, stddev=0.001),
[…]

### 2016-12-16 practical_3/methenitis_assignment_3/vgg.py

@@ -1,0 +1,282 @@
+import tensorflow as tf
+import numpy as np
+
+VGG_FILE = './pretrained_params/vgg16_weights.npz'
+
+def load_pretrained_VGG16_pool5(input, scope_name='vgg'):
+    """
+    Load an existing pretrained VGG-16 model.
+    See https://www.cs.toronto.edu/~frossard/post/vgg16/
+
+    Args:
+        input:         4D Tensor, Input data
+        scope_name:    Variable scope name
+
+    Returns:
+        pool5: 4D Tensor, last pooling layer
+        assign_ops: List of TF operations, these operations assign pre-trained values
+                    to all parameters.
+    """
+
+    with tf.variable_scope(scope_name):
+
+        vgg_weights, vgg_keys = load_weights(VGG_FILE)
+
+        assign_ops = []
+        # conv1_1
+        with tf.name_scope('conv1_1') as scope:
+            vgg_W = vgg_weights['conv1_1_W']
+            vgg_B = vgg_weights['conv1_1_b']
+            kernel = tf.get_variable('conv1_1/' + 'weights', vgg_W.shape,
+                                     initializer=tf.random_normal_initializer())
+
+            assign_ops.append(kernel.assign(vgg_W))
+            conv = tf.nn.conv2d(input, kernel, [1, 1, 1, 1], padding='SAME')
+            biases = tf.get_variable('conv1_1/' + "biases", vgg_B.shape,
+                initializer=tf.constant_initializer(0.0))
+
+            assign_ops.append(biases.assign(vgg_B))
+            out = tf.nn.bias_add(conv, biases)
+            conv1_1 = tf.nn.relu(out, name=scope)
+
+
+        # conv1_2
+        with tf.name_scope('conv1_2') as scope:
+            vgg_W = vgg_weights['conv1_2_W']
+            vgg_B = vgg_weights['conv1_2_b']
+            kernel = tf.get_variable('conv1_2/' + 'weights', vgg_W.shape,
+                                     initializer=tf.random_normal_initializer())
+
+            assign_ops.append(kernel.assign(vgg_W))
+
+            conv = tf.nn.conv2d(conv1_1, kernel, [1, 1, 1, 1], padding='SAME')
+            biases = tf.get_variable('conv1_2/' + "biases", vgg_B.shape,
+                                    initializer=tf.constant_initializer(0.0))
+
+            assign_ops.append(biases.assign(vgg_B))
+            out = tf.nn.bias_add(conv, biases)
[…]
